### 2022-03-06 article_summaries.Rmd
Added article summeries.

---
title: "Article Summaries"
author: "Skip Moses"
date: "2/26/2022"
output: html_document
bibliography: ref.bib 
cls: IEEEtran.cls
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Literature Review

Data often has  an underlying structure or Geometry that can be modeled as a signal on the vertices of a weighted, undirected graph. Traditionally, the emphasis was on using a the underlying graph, or network, to understand the properties of signals over the vertices. Recently, there has been a surge in converse problem; of learning a graph structure from a set of signals satisfying some something constraints @xia2021graph @stankovic2019vertex @ortega2018graph . The subset of Graph Learning that focuses on Graph Signal Processing Based Methods deals with sampling, graph recovery and learning topological structure @xia2021graph . The methods for learning topolological structure fall into the categories of supervised models @dong2016learning @tugnait2021sparse @pu2021learning @saboksayr2021accelerated, and unsupervised machine learning techniques @pu2021kernel @kalofolias2016learn @venkitaraman2019predicting . In all of these models, signals are assumed to follow multivariate gaussian distributions, but there has been little to know literature exploring learing network topology from binomial signals.

## Graph Learning: A Survey

#### Feng Xia,  Ke Sun , Shuo Yu, Abdul Aziz,

#### Liangtian Wan,  Shirui Pan , and Huan Liu

Graphs, or networks, can model numerous real-world relationships. For example, social networks, biological networks, patent networks, traffic networks, citation networks, and communication networks. In all of these cases, the graphs are known a priori. Recently, Graph Learning has become a popular approach to extracting meaningful relationships from data sets where the graph is not otherwise known.

In essence, graph learning is a form of machine learning on graphs. Most methods of graph learning take the features of the graph into a vector space with the same dimensions. This is accomplished without projecting the graph into a low dimensional space. The representation of the graph can be utilized without an explicit embedding. This is what makes graph learning such a powerful technique.

Graph learning can be partitioned into four fields:

  1. Graph Signal Processing Based Methods

Deals with sampling, graph recovery and learning topological structure.

  2. Random Walk Based Methods

Includes structure-based random walk, structure and node information based random walk, random walk in heterogeneous networks and random walk in time-varying networks.

  3. Matrix Factorization Based Methods

Deals with Laplacian matrix factorization and vertex proximity matrix factorization.

  4. Deep Learning Based Methods

Includes graph convolutional networks, graph attention networks, graph auto-encoder, graph generative networks and graph spatial-temporal networks.

The main difference in these four methods/techniques is in their model architecture.

Traditional signal processing has been very successful in analyzing signals from a regular data domain. Graphs represent a kind of irregular data; this makes appling tradional methods hard. Thus, the main task of GSP is to generalize traditional signal processing techinques into this irregular domain. There are two main approaches to representing a graph in GSP; Adjacency based GSP and Laplacian based GSP. Adjacency based techniques are grounded in algebraic signal processin (ASP). Laplacian based techniques are derived from spectral graph theory. The Laplacian (or Adjacency matrix) take on the roll of a shift operator in traditional signal processing.

## Sparse Graph Learning Under Laplacian-Related Constraints

#### Jitendra K. Tugnait

A sparse undirected graph under graph Laplacian-related contraints on the sparse precision matrix is learned. The off diagonal elements of the precision matrix are forced to be non-positive, but the precision matrix is not assumed to be full rank. In short, this method is a modification to traditional penalized log-likelihood approaches but not forcing an explicit Laplacian structure. The graph Laplacian is recovered from the off diagonal of the precision matrix. The method was shown to outperform existing Laplacian based approaches in expiremental settings. The method was also successfully applied to finacial time series data by considering 97 stocks in S&P 100 index from Jan. 1, 2013 through Jan. 1 2018. Theoretical results only hold under the assumption the precision matrix is postive definite.

## Learning to Learn Graph Topologies

#### Xingyue Pu, Tianyue Cao, Xiaoyun Zhang, Xiaowen Dong, Siheng Chen

In model-based graph learning learning a graph topology is reduced to an optimisation problem over the space of graphs whose objective function carries the inductive graph-data interactions. The objective function typically consit of a graph-data fidelity term and a structural regulariser. 
Convex optimisation problems can be solved by iterative algorithms with convergence guarnetees.

The main limitation of these methods is convex regularisers are not capapble of expressing rich topological and structural priors. Complex properties like scale-free and small-world properties have not been explored in detail due to lack of expressibility in a convex program. Some other limitations include the scalability of iterative algorithms and tuning parameters is computationally laborious.

To address these shortcomings, a novel functional learning framework to learn an underlying graph topology with desired structural property. This framework is based on the field of learning to optimise (L2O). In order to learn to learn a graph topology a neural network that maps data terms to graph representations with identical topological properties.

The method is applied to S&P 100 Stock Returns and Assitant Diagnosis of Autism real world data sets.

## Accelerated Graph Learning from Smooth Signals

#### Seyed Saman Saboksayr

A fast scalable learning framework is created by utilizing fast proximal gradient iterations (PG). Unlike other used solvers, primal-dual method and alternating-direction method of multipliers, PG has global convergence rate guarentees and does not require additional step-size tuning. Simulated data is used to confirm favoriable convergence rates. The proposed framework is tested on real-world graphs with synthetic signals. The focus of this paper is on convergence rates, so the quality of learned graph is not measured.

# References

<div id="refs"></div>

### 2022-03-13 draft.Rmd
added draft file and made recommended changes to introduction.

---
title: 'Draft: Learning Laplacian from Binomial Signals'
author: "Skip Moses"
date: "3/12/2022"
output: html_document
bibliography: ref.bib 
cls: IEEEtran.cls
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Data often has  an underlying structure or geometry that can be modeled as a signal on the vertices of a weighted, undirected graph. Traditionally, the emphasis was on using a underlying graph, or network, to understand the properties of signals over the vertices. Recently, there has been a surge in converse problem; of learning a graph structure from a set of signals satisfying some constraints @xia2021graph @stankovic2019vertex @ortega2018graph . A subset of graph learning that focuses on graph signal processing based methods deals with sampling, graph recovery and learning topological structure @xia2021graph.

The methods for learning topological structure fall into the categories of regression like models @dong2016learning, @tugnait2021sparse, @pu2021learning, and @saboksayr2021accelerated, and machine learning techniques @pu2021kernel, @kalofolias2016learn, and  @venkitaraman2019predicting . In all of these models, signals are assumed to follow multivariate gaussian distributions, but there has been little exploration in learning a network from binomial signals.

## Related Work

Dong et al. propose a modified Factor Analysis model in @dong2016learning for learning a valid graph laplacian. The model proposed is given by 
$$x = \chi h + \mu_x + \epsilon$$
where $h \in \mathbb{R}^N$ is the latent variable, $\mu_x \in \mathbb{R}^N$ mean of $x$. The noise term $\epsilon$ is assumed to follow a multivariate Gaussian distribution with mean zero and covariance $\sigma_\epsilon^2I_N$. The key difference from traditional factor analysis is the choice of $\chi$ as a valid eigenvector matrix for a graph laplacian. Finding a maximum apriori estimate of $h$ reduces to solving the optimization problem

\begin{equation}
	\label{eq:dongmodel}
	\begin{aligned}
		\min_{L \in \mathbb{R}^{N\times N}, \phantom{..} Y \in \mathbb{R}^{N\times P}} ||X&-Y||_F^2 + \alpha \text{tr}(Y^TLY) + \beta||L||_F^2 \\
		\textrm{s.t.}& \quad \text{tr}(L) = N, \\
		&\quad L_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j, \\
		&\quad L\cdot \textbf{1} = \textbf{0} \\
	\end{aligned}
\end{equation}

Because \ref{eq:dongmodel} is not jointly convex, Dong et al. employ an alternating minimization scheme to solve the problem. Initially, set $Y = X$ and we find a suitable $L$ by solving 
\begin{equation}
	\label{eq:dong:prob1}
	\begin{aligned}
		\min_L       & \phantom{..} \alpha \text{tr}(Y^TLY) + \beta ||L||_F^2, \\
		\textrm{s.t.}& \quad \text{tr}(L) = N,\\
					 & \quad L_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j, \\
					 & \quad L\cdot \textbf{1} = \textbf{0}
	\end{aligned}
\end{equation}

Next, using $L$ from the first step we solve 
\begin{equation}
	\label{eq:dong:prob2}
	\begin{aligned}
		\min_Y \phantom{..} ||X-Y||_F^2 + \alpha \text{tr}(Y^TLY)
	\end{aligned}
\end{equation}

Both \ref{eq:dong:prob1} and \ref{eq:dong:prob2} can be cast as convex optimization problems. Specifically, \ref{eq:dong:prob1} can be solved with the method of alternating direction of multipliers (ADMM). The model is applied to both synthetic and real world data, and compared to a technique used in machine learning that is similar to sparse inverse covariance estimation of Gaussian Markov Random Field models. Four evaluation criteria were used  to evaluate the performance of the framework: $\textit{Precision, Recall, F-measure,}$ and $\textit{Normalized Mutual Information (NMI)}$. Kalofolias cites two weaknesses to this model: The use of the Frobenius norm is not amenable to interpretation, and it requires four constraints on the solution space @kalofolias2016learn.

In @kalofolias2016learn, Kalofolias provides complementary ideas to improve on the work of Dong et al. In particular, Kalofolias considers the more natural problem of leaning the weighted adjacency matrix $A$, and show an extra smoothness condition leads to the learned graph being sparse. Define, $Z$ to be the matrix of pairwise distances of the signal, namely, $Z_{i,j} = ||x_i - x_j||^2$. Under this definition we can recast our smoothness term as 
\begin{equation}
	\label{eq:kalotransform}
	\text{tr}(X^TLX) = \frac{1}{2} \text{tr}(AZ) = \frac{1}{2}  ||A\circ Z||_{1,1};
\end{equation}
where $\circ$ is the hadamard product and $||A||_{1,1}$ is the element wise 1-norm. We can now recast \ref{eq:GLP} as 
\begin{equation}
	\label{eq:GLP}
	\begin{aligned}
		\min_A       & \phantom{..} ||A\circ Z||_{1,1} + f(A), \\
		\textrm{s.t.}& \quad ||A||_{1,1} = N,\\
		& \quad A_{i,j} = A_{j,i} \geq 0, \phantom{..} i \neq j, \\
		& \quad \text{diag}(A) = \textbf{0}
	\end{aligned}
\end{equation}

The model proposed by Kalofolias is given by specifying $f(A) = -\alpha \textbf{1}^T\log(W\textbf{1}) + \beta||W||_F^2$. An appealing feature of this model is the fact that for any $\lambda >0$ and solution $F(Z,\alpha, \beta)$ the following equalities hold
\begin{equation}
	\label{eq:KalofoliasEquality}
	F(Z, \alpha, \beta) = \lambda F(Z, \frac{\alpha}{\lambda}, \beta \lambda) = \alpha F(Z, 1, \alpha \beta).
\end{equation}
This means we can fix a scale $||A|| = s$ for an arbitrary norm and solve for $\beta$ in \ref{eq:kalotransform} with $\alpha = 1$, and then re-normalize our solution. Furthermore, the log barrier term only acts on the degrees. This provides an advantage over the model \ref{eq:dongmodel}, because it promotes connectivity in the learned graph. Kalofolias goes onto show \ref{eq:kalotransform} can be solved efficiently for many choices of $f(A)$ via primal dual algorithms.

In @venkitaraman2019predicting machine learning concepts are employed to learn a graph from training data. The goal is given some data ${x_n}$ to model a target $t_n$ by the linear basis model for regression
\begin{equation}
	\label{eq:LinearModel}
	y_n = \textbf{W}^T\phi(x_n),
\end{equation}
where $\phi(x_n)$ is some known function and $\textbf{W}$ denotes the regression coefficient matrix. Venkitarman et al. assume only the target $y_n$ is smooth over the graph. The input $x_n$ does not have to be a signal over the graph and can even be agnostic to a graph. The cost function for the model when the underlying graph is known is given by 
\begin{equation}
	\label{eq:cost}
	C(\textbf{W}) = \sum_{n=1}^N\left( ||t_n - y_n||_2^2 + \beta y_n^TLy_n \right) + \alpha \text{tr}(\textbf{W}^T\textbf{W}).
\end{equation}
Next, it is shown KRG induces a smoothing effect on the target by a shrinkage in the direction of eigenvectors of $L$ that have eigenvalues less than $\alpha$. In order to learn an unknown graph, a term is added to the cost function $C(\textbf{W}, L) = C(\textbf{W}) + \nu \text{tr}(L^TL)$.  Venkitarman et al. use the model to predict temperature using air-pressure observations collected in Sweden, next day temperature from current day in Sweden, and fMRI voxel intensities of the cerebellum region. The latter two experiments are compared the method of kernel-ridge regression (KRR) by using a normalized-mean-square-error to measure the performance of the prediction. It is concluded that the method is well suited for training with noise data sets that may be small.

## Preliminaries

A weighted, undirected graph is a triple $G = (V, E, \omega)$ of two sets $V = \{1, \ldots, |V| = N \}$ and $E \subset V \times V$ and a weighting function $\omega(i,j) = \omega_{i,j}$ that assigns a non-negative real number to each edge. We can represent a graph by its adjacency matrix $A$ where $A_{i,j} = \omega_{i,j}$ if $(i,j) \in E$ and $0$ otherwise. A signal on a graph $G$ is a function $f: V \rightarrow \mathbb{R}$ that can be represented as vector $x \in \mathbb{R}^N$. The Laplacian of a graph is the matrix $L = D - A$ where $D$ is the degree matrix. The Laplacian acts as a difference operator on signals via it's quadratic form
\begin{equation}
	\label{eq:quadraticform}
	x^TLx = \sum_{(i,j)\in E}A_{i,j}(x_j - x_i)^2.
\end{equation} 
The Laplacian is positive semi definite, so it has a complete set of orthornormal eigenvectors, and real non negative eigenvalues. Thus, we can diagonalize $L = \chi^T\Lambda \chi$ where $\Lambda$ is the diagonal matrix of eigenvalues and $\chi$ is associated matrix of eigenvectors.

Note that \ref{eq:quadraticform} is minimized when adjacent vertices have identical signal values. This makes \ref{eq:quadraticform} well suited for measuring the smoothness of a signal on a graph. We can cast the problem of learning a graph by the optimization problem found in \cite{kalofolias2016learn}
\begin{equation}
	\label{eq:GLP}
	\begin{aligned}
		\min_L       & \phantom{..} \text{tr}(Y^TLY) + f(L), \\
		\textrm{s.t.}& \quad \text{tr}(L) = N,\\
		& \quad L_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j, \\
		& \quad L\cdot \textbf{1} = \textbf{0}
	\end{aligned}
\end{equation}

### 2022-03-15 draft.Rmd
Updates to draft.

@@
 date: "3/12/2022"
-output: html_document
+output: pdf_document
 bibliography: ref.bib 
@@
 This makes \ref{eq:quadraticform} well suited for measuring the smoothness of a signal on a graph.
-We can cast the problem of learning a graph by the optimization problem found in \cite{kalofolias2016learn}
+We can cast the problem of learning a graph by the optimization problem found in @kalofolias2016learn
 \begin{equation}
@@
 \end{equation}
+
+## Our Model
+
+In order to generalize our model, we will take inspiration from the ideas used to generalize linear regression to logistic regression.
+Let $p(x = 1)$ be the probability a signal value of $1$ is observed on node $x$.
+Our model will be of the form
+\begin{align}
+\text{logit}(p) = \chi h + p(x = 1) + \epsilon
+\end{align}
+
+Where $\chi$ is our matrix of eigenvalues for our graph. Recall, in binomial distribution the expectation is exactly $p(x = 1)$.
+
+## Discussion
+
+Currently, GSP frameworks such as ours have limitations making them only practical in experimental settings.
+For instance, these frameworks require the input to be the entire graph.
+This automatically puts a harsh limit on the size of the graphs that can be learned.
+Another related limitation, is the availability of the algorithms used to learn the laplacian.
+In @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn converges to a globally optimal solution in $O (1/k)$.
+A natural next step would be to apply fast proximal-gradient iterations our framework to overcome scalability issues.
+
+## References
+<div id="refs"></div>

### 2022-04-03 Scripts/gl_sig_rep/graph_learning_gaussian.py
add cholesky factorization in graph_learning_gaussian function

@@ -23,10 +23,12 @@ def graph_learning_gaussian(X_noisy, param):
         L = olg.optimize_laplacian_gaussian(N,Y,alpha,beta)
         
         # Step 2: given L, update Y
-        R = (np.identity(N) + alpha*L)
+        R = np.linalg.cholesky(np.identity(N) + alpha*L)
         Rt = np.transpose(R)
-        arg1 = np.linalg.lstsq(Rt, Y_0, rcond=None)[0].round(4)
-        Y = np.linalg.lstsq(R, arg1, rcond=None)[0].round(4)
+        arg1 = np.linalg.lstsq(Rt, Y_0)[0]
+        print('arg1 shape is ' + str(arg1.shape))
+        print('R shape is ' + str(R.shape))
+        Y = np.linalg.lstsq(R, arg1)[0]
         
         # Store objective
         arg1 = np.linalg.norm(Y-Y_0, 'fro')**2 

### 2022-04-06 model specification.Rmd
add model specification file discussed 4-5-2022

---
title: "Comments on binomial graph learning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Inspired by conditional logistic regression 
Let $Y_{i,j}$ denote the measurement on the node $i$ at round $j$, where $j = 1, \dots, M$, and $i = 1, \dots, N$. $Y_{i,j}$ is a binomial signal that can be 1, or 0. (complete signals for each node. might be revised ) Suppose the signals at round $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at round $k$ denoted by $Y[,k ]$, for $i \neq k$. Let $p_{i,j}$ denote the probability of $Y_{i,j} = 1$. Our model assumes
$$logit(p_{i,j}) = \alpha_j + (\chi h )_i,$$

where $\chi$ is the eigenvector matrix from Graph Laplacian $L$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\chi$ (might be changed to get a nice solution), and $\alpha_j$ is a round specific parameter at round $j$.
Constraints:

Sigmoid computation,
Bound and Branch method of optimization

hint for factor analysis solution might be useful because there is another object function varimax.

https://conservancy.umn.edu/bitstream/handle/11299/95957/Choi_umn_0130E_11451.pdf?sequence=1&isAllowed=y

https://web.stanford.edu/~boyd/papers/pdf/max_sum_sigmoids.pdf

* complete separation do not exist. observable metric ?, it is a potential new topic to be able to identify whether complete separation exists. possible discuss it in the Discussion and future work.

* While working on this one, you may also consider implementing our regressor paper.

## Our goal is to estimate the Graph Laplacian

* We do not have to use the eigenvector matrix $\chi$. Instead, we may consider adjacency matrix $A$ in place of $\chi$. This is a viable direction.

Maximum Likelihood estimation, Quasi likelihood estimation,

### 2022-04-10 model specification.Rmd
update model specification binary graph learning

@@
 title: "Comments on binomial graph learning"
-output: html_document
+output: pdf_document
 ---
@@
 
-## Inspired by conditional logistic regression 
+## Binary graph learning model 
+### Version 1 (Eigenvector matrix from Graph Laplacian)
 Let $Y_{i,j}$ denote the measurement on the node $i$ at round $j$, where $j = 1, \dots, M$, and $i = 1, \dots, N$.
 $Y_{i,j}$ is a binomial signal that can be 1, or 0.
-(complete signals for each node.
-might be revised ) Suppose the signals at round $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at round $k$ denoted by $Y[,k ]$, for $i \neq k$.
+Suppose the signals at round $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at round $k$ denoted by $Y[,k ]$, for $i \neq k$.
 Let $p_{i,j}$ denote the probability of $Y_{i,j} = 1$.
 Our model assumes
-$$logit(p_{i,j}) = \alpha_j + (\chi h )_i,$$
+$$\text{logit}(p_{i,j}) = \alpha_j + (\chi h )_i,$$
 
-where $\chi$ is the eigenvector matrix from Graph Laplacian $L$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\chi$ (might be changed to get a nice solution), and $\alpha_j$ is a round specific parameter at round $j$.
+where $\chi$ is the eigenvector matrix from Graph Laplacian $L$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\chi$, and $\alpha_j$ is a round specific parameter at round $j$.
+
+### Version 2 (Adjacency matrix from Graph)
+#### Graph 
+We consider a weighted undirected graph $G = (V, E)$, with the vertices set $V = {1, 2, \dots, N}$, and edge set $E$.
+Let $\mathbf{A}$ denote the weighted adjacency matrix for the graph $G$.
+In the case of weighted undirected graph, $\mathbf{A}$ is a square and symmetric matrix.
+
+#### Signals on the graph
+Let $Y_{i,j}$ denote the signal on the node $i$ of graph $G$ at round $j$, where $j = 1, \dots, M$, and $i = 1, \dots, N$.
+We assume that $Y_{i,j}$ is a binary signal that can be 1, or 0.
+Suppose the signals at round $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at round (or strata) $k$ denoted by $Y[,k ]$, for $i \neq k$, borrowing the idea of conditional logistic regression.
+Let $p_{i,j}$ denote the probability of $Y_{i,j} = 1$.
+Our model assumes
+
+\begin{equation}
+\label{eq:binaryglm}
+\text{logit}(p_{i,j}) = \alpha_j + (\mathbf{A} h )_i,
+\end{equation}
+
+where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$, and $\alpha_j$ is a round specific parameter at round or strata $j$.
+In the following, we will use
+
+## Method of Estimation
+
+The conditional likelihood function for model (\ref{eq:binaryglm}) given  is (I will update soon)
+
+<!-- \begin{equation} -->
+<!-- 	\label{eq:dongmodel} -->
+<!-- 	\begin{aligned} -->
+<!-- 		\min_{L \in \mathbb{R}^{N\times N}, \phantom{..} Y \in \mathbb{R}^{N\times P}} ||X&-Y||_F^2 + \alpha \text{tr}(Y^TLY) + \beta||L||_F^2 \\ -->
+<!-- 		\textrm{s.t.}& \quad \text{tr}(L) = N, \\ -->
+<!-- 		&\quad L_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j, \\ -->
+<!-- 		&\quad L\cdot \textbf{1} = \textbf{0} \\ -->
+<!-- 	\end{aligned} -->
+<!-- \end{equation} -->
+
+## Miscellaneous 
 Constraints:
@@
 
+## Model Specification
+
 ## Our goal is to estimate the Graph Laplacian

### 2022-04-12 model specification.Rmd
Added constraints.
Updates to visuals and constraints.

@@
 
+* Case $\chi$: Here I imagine the constraints are on the Laplacian
+
+\begin{equation}
+\begin{aligned}
+&\quad \text{tr}(L) = N, \\
+&\quad L_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j, \\
+&\quad L\cdot \textbf{1} = \textbf{0} \\
+\end{aligned}
+\end{equation}
+
+* Case with adjacency matrix:
+
+\begin{equation}
+\begin{aligned}
+&\quad A_{i,j} = 0 \text{ if } i = j, \\
+&\quad A_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j
+\end{aligned}
+\end{equation}
+
+* Consider the quadratic form 
+$$
+  x^TLx = \frac{1}{2}\sum_{(i,j)\in E}w_{i,j}(f(i) - f(j))^2
+$$
+
+Because $x$ is a binomial, this expression sums the weights of edeges with incident nodes that have differing signal values.
+Suppose the graph has a constant signal, then $x^TLx = 0$.
+Suppose, we are in the worst case when incident nodes for each edge have a different signal; in this case $x^TLx = \frac{1}{2}\sum_{(i,j) \in E}w_{i,j}$.
+Note, we can bound $x^TLx$ from below by $\min{w_{i,j}}$ in the case were a single edge has incident nodes with differing signals.
+We can use these bounds to gauge the quality of model.
+
 Sigmoid computation,

### 2022-04-12 Scripts/gl_sig_rep/graph_learning_gaussian.py

@@ -26,8 +26,8 @@ def graph_learning_gaussian(X_noisy, param):
         R = np.linalg.cholesky(np.identity(N) + alpha*L)
         Rt = np.transpose(R)
         arg1 = np.linalg.lstsq(Rt, Y_0)[0]
-        print('arg1 shape is ' + str(arg1.shape))
-        print('R shape is ' + str(R.shape))
+        # print('arg1 shape is ' + str(arg1.shape))
+        # print('R shape is ' + str(R.shape))
         Y = np.linalg.lstsq(R, arg1)[0]
         
         # Store objective

### 2022-04-12 model specification.Rmd
update model specification

@@
 We assume that $Y_{i,j}$ is a binary signal that can be 1, or 0.
-Suppose the signals at round $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at round (or strata) $k$ denoted by $Y[,k ]$, for $i \neq k$, borrowing the idea of conditional logistic regression.
+Suppose the signals at round $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at round (or stratum) $k$ denoted by $Y[,k ]$, for $i \neq k$, borrowing the idea of conditional logistic regression.
 Let $p_{i,j}$ denote the probability of $Y_{i,j} = 1$.
@@
 
-where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$, and $\alpha_j$ is a round specific parameter at round or strata $j$.
+where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$ and assumed to be a standard normal random vector, and $\alpha_j$ is a round specific parameter at round or stratum $j$.
 In the following, we will use
@@
 ## Method of Estimation
+### Conditional likelihood for one stratum
+Let $O_i$ denote the set of nodes at stratum $i$ that have observed signals of 1, and let $Z_i$ denote the set of nodes at stratum $i$ that have observed signals of 0.
+Suppose the number of nodes that have signals of 1 at stratum $i$ is $k_i$.
+The conditional likelihood function based on model (\ref{eq:binaryglm}) for one stratum $i$ of size $N$, is
 
-The conditional likelihood function for model (\ref{eq:binaryglm}) given  is (I will update soon)
+\begin{equation}
+	\label{eq:stratumlikelihood}
+	\begin{aligned}
+	&	P(Y_{il} = 1 \text{ for } l \in O_i, Y_{im} = 0 \text{ for } m \in Z_i | \sum_{j=1}^M Y_{ij} = k_i) \\   
+	& =  {\text{exp} (\sum_{l \in O_i}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_i}^M} \text{exp} (\sum_{j \in J}\mathbf{A}[j, ] h  },
+	\end{aligned}
+\end{equation}
+
+where $C_{k_i}^M$ is the set of all subsets of size $k_i$ of the set ${1, 2, \dots, M}$.
+
+### Conditional log likelihood function
+The full conditional log likelihood function is the sum of the log likelihoods for each stratum and can be written as
 
 <!-- \begin{equation} -->
-<!-- 	\label{eq:dongmodel} -->
+<!-- 	\label{eq:condloglikelihood} -->
 <!-- 	\begin{aligned} -->
-<!-- 		\min_{L \in \mathbb{R}^{N\times N}, \phantom{..} Y \in \mathbb{R}^{N\times P}} ||X&-Y||_F^2 + \alpha \text{tr}(Y^TLY) + \beta||L||_F^2 \\ -->
-<!-- 		\textrm{s.t.}& \quad \text{tr}(L) = N, \\ -->
-<!-- 		&\quad L_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j, \\ -->
-<!-- 		&\quad L\cdot \textbf{1} = \textbf{0} \\ -->
+<!-- 	&	P(Y_{il} = 1 \text{ for } l \in O_i, Y_{im} = 0 \text{ for } m \in Z_i | \sum_{j=1}^M Y_{ij} = k_i) \\    -->
+<!-- 	& =  {\text{exp} (\sum_{l \in O_i}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_i}^M} \text{exp} (\sum_{j \in J}\mathbf{A}[j, ] h  }, -->
 <!-- 	\end{aligned} -->
@@
 &\quad A_{i,j} = 0 \text{ if } i = j, \\
-&\quad A_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j
+&\quad A_{i,j} = A_{j,i} \geq 0, \phantom{..} \text{ if } i \neq j
 \end{aligned}

### 2022-04-13 model specification.Rmd
add model specification

@@
 ### Conditional likelihood for one stratum
-Let $O_i$ denote the set of nodes at stratum $i$ that have observed signals of 1, and let $Z_i$ denote the set of nodes at stratum $i$ that have observed signals of 0.
-Suppose the number of nodes that have signals of 1 at stratum $i$ is $k_i$.
-The conditional likelihood function based on model (\ref{eq:binaryglm}) for one stratum $i$ of size $N$, is
+Let $O_j$ denote the set of nodes at stratum $j$ that have observed signals of 1, and let $Z_j$ denote the set of nodes at stratum $j$ that have observed signals of 0.
+Suppose the number of nodes that have signals of 1 at stratum $j$ is $k_j$.
+The conditional likelihood function based on model (\ref{eq:binaryglm}) for stratum $j$ of size $N$, is
 
@@
 	\begin{aligned}
-	&	P(Y_{il} = 1 \text{ for } l \in O_i, Y_{im} = 0 \text{ for } m \in Z_i | \sum_{j=1}^M Y_{ij} = k_i) \\   
-	& =  {\text{exp} (\sum_{l \in O_i}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_i}^M} \text{exp} (\sum_{j \in J}\mathbf{A}[j, ] h  },
+	&	P(Y_{lj} = 1 \text{ for } l \in O_j, Y_{mj} = 0 \text{ for } m \in Z_j | \sum_{i=1}^N Y_{ij} = k_j) \\   
+	& =  {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
 	\end{aligned}
@@
 
-where $C_{k_i}^M$ is the set of all subsets of size $k_i$ of the set ${1, 2, \dots, M}$.
+where $C_{k_j}^N$ is the set of all subsets of size $k_j$ of the set ${1, 2, \dots, N}$.
+
+### Conditional likelihoood function
+The conditional likelihood function for all strata is written as
+\begin{equation}
+	\label{eq:conlikelihood}
+	\begin{aligned}
+	&	L(\mathbf{A}, \beta)  = \prod_{j=1}^M {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
+	\end{aligned}
+\end{equation}
 
@@
 
-<!-- \begin{equation} -->
-<!-- 	\label{eq:condloglikelihood} -->
-<!-- 	\begin{aligned} -->
-<!-- 	&	P(Y_{il} = 1 \text{ for } l \in O_i, Y_{im} = 0 \text{ for } m \in Z_i | \sum_{j=1}^M Y_{ij} = k_i) \\    -->
-<!-- 	& =  {\text{exp} (\sum_{l \in O_i}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_i}^M} \text{exp} (\sum_{j \in J}\mathbf{A}[j, ] h  }, -->
-<!-- 	\end{aligned} -->
-<!-- \end{equation} -->
+\begin{equation}
+	\label{eq:condloglikelihood}
+	\begin{aligned}
+	&	\text{log}(L(\mathbf{A}, \beta))  = \sum_{j=1}^M \sum_{l \in O_j}\mathbf{A}[l, ] h  - \sum_{j=1}^M \text{log}\sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) ,
+	\end{aligned}
+\end{equation}
 

### 2022-04-18 abstract.Rmd
Added abstract.

---
title: "Abstract"
author: "Skip Moses"
date: "4/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data often has an underlying structure of Geometry that can be modeled a signal on the vertices of a weighted, undirected graph. There are several analogies between traditional signal processing an algebraic graph theory that translates many of the tools of discrete signal processing such as spectral analysis of multichannel signals, system transfer function, and digital filter design to name a few. Historically, GSP has focused on modeling smooth signals on a graph, but the increase in availability of abstract data sets has motivated algorithms for learning a valid graph given a set of signals. In this work we attempt to design such an algorithm for learning a valid graph topology given a set of binomial signals. This is accomplished by extending the ideas of Conditional Logistic Regression and Maximum Likelihood with constraints that enforce a valid graph topology on the regression coefficient matrix.

### 2022-04-19 model specification.Rmd
add poster and fix model specification

@@
 
-where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$ and assumed to be a standard normal random vector, and $\alpha_j$ is a round specific parameter at round or stratum $j$.
-In the following, we will use
+where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$ and assumed to be a standard normal random vector, and $\alpha_j$ is a round specific parameter at round or stratum $j$, and assumed to be normally distributed with mean of 0, and unknown variance $\sigma^2$
 
@@
 	\begin{aligned}
-	&	L(\mathbf{A}, \beta)  = \prod_{j=1}^M {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
+	&	L(\mathbf{A}, h)  = \prod_{j=1}^M {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
 	\end{aligned}
@@
 	\begin{aligned}
-	&	\text{log}(L(\mathbf{A}, \beta))  = \sum_{j=1}^M \sum_{l \in O_j}\mathbf{A}[l, ] h  - \sum_{j=1}^M \text{log}\sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) ,
+	&	\text{log}(L(\mathbf{A}, h))  = \sum_{j=1}^M \sum_{l \in O_j}\mathbf{A}[l, ] h  - \sum_{j=1}^M \text{log}\sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) 
+	& = \sum_{j=1}^M \mathbf{A} h y_j  - \sum_{j=1}^M \text{log}\sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h )
 	\end{aligned}
 \end{equation}
+
+### The Estimator
+The maximum likelihood estimator is then defined as $\mathbf{A}$ which maximize (\ref{eq:condloglikelihood}), which is equivalent to minimizing the negative conditional log likelihood.
 

### 2022-04-20 model-specification.tex
Update Poster

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Comments on binomial graph learning},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Comments on binomial graph learning}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\hypertarget{binary-graph-learning-model}{%
\subsection{Binary graph learning
model}\label{binary-graph-learning-model}}

\hypertarget{version-1-eigenvector-matrix-from-graph-laplacian}{%
\subsubsection{Version 1 (Eigenvector matrix from Graph
Laplacian)}\label{version-1-eigenvector-matrix-from-graph-laplacian}}

Let \(Y_{i,j}\) denote the measurement on the node \(i\) at round \(j\),
where \(j = 1, \dots, M\), and \(i = 1, \dots, N\). \(Y_{i,j}\) is a
binomial signal that can be 1, or 0. Suppose the signals at round \(j\)
denoted by \(Y[, j]\) for all \(N\) nodes are independent of the signals
at round \(k\) denoted by \(Y[,k ]\), for \(i \neq k\). Let \(p_{i,j}\)
denote the probability of \(Y_{i,j} = 1\). Our model assumes
\[\text{logit}(p_{i,j}) = \alpha_j + (\chi h )_i,\]

where \(\chi\) is the eigenvector matrix from Graph Laplacian \(L\),
\(h\) is a vector of latent factors that governs \(p_{i, j}\) through
\(\chi\), and \(\alpha_j\) is a round specific parameter at round \(j\).

\hypertarget{version-2-adjacency-matrix-from-graph}{%
\subsubsection{Version 2 (Adjacency matrix from
Graph)}\label{version-2-adjacency-matrix-from-graph}}

\hypertarget{graph}{%
\paragraph{Graph}\label{graph}}

We consider a weighted undirected graph \(G = (V, E)\), with the
vertices set \(V = {1, 2, \dots, N}\), and edge set \(E\). Let
\(\mathbf{A}\) denote the weighted adjacency matrix for the graph \(G\).
In the case of weighted undirected graph, \(\mathbf{A}\) is a square and
symmetric matrix.

\hypertarget{signals-on-the-graph}{%
\paragraph{Signals on the graph}\label{signals-on-the-graph}}

Let \(Y_{i,j}\) denote the signal on the node \(i\) of graph \(G\) at
round \(j\), where \(j = 1, \dots, M\), and \(i = 1, \dots, N\). We
assume that \(Y_{i,j}\) is a binary signal that can be 1, or 0. Suppose
the signals at round \(j\) denoted by \(Y[, j]\) for all \(N\) nodes are
independent of the signals at round (or stratum) \(k\) denoted by
\(Y[,k ]\), for \(j \neq k\), borrowing the idea of conditional logistic
regression. Let \(p_{i,j}\) denote the probability of \(Y_{i,j} = 1\).
Our model assumes

\begin{equation}
\label{eq:binaryglm}
\text{logit}(p_{i,j}) = \alpha_j + (\mathbf{A} h )_i,
\end{equation}

where \(\mathbf{A}\) is the adjacency matrix from the graph \(G\), \(h\)
is a vector of latent factors that governs \(p_{i, j}\) through
\(\mathbf{A}\) and assumed to be a standard normal random vector, and
\(\alpha_j\) is a round specific parameter at round or stratum \(j\),
and assumed to be normally distributed with mean of 0, and unknown
variance \(\sigma^2\)

\hypertarget{method-of-estimation}{%
\subsection{Method of Estimation}\label{method-of-estimation}}

\hypertarget{conditional-likelihood-for-one-stratum}{%
\subsubsection{Conditional likelihood for one
stratum}\label{conditional-likelihood-for-one-stratum}}

Let \(O_j\) denote the set of nodes at stratum \(j\) that have observed
signals of 1, and let \(Z_j\) denote the set of nodes at stratum \(j\)
that have observed signals of 0. Suppose the number of nodes that have
signals of 1 at stratum \(j\) is \(k_j\). The conditional likelihood
function based on model (\ref{eq:binaryglm}) for stratum \(j\) of size
\(N\), is

\begin{equation}
    \label{eq:stratumlikelihood}
    \begin{aligned}
    &   P(Y_{lj} = 1 \text{ for } l \in O_j, Y_{mj} = 0 \text{ for } m \in Z_j | \sum_{i=1}^N Y_{ij} = k_j) \\   
    & =  {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
    \end{aligned}
\end{equation}

where \(C_{k_j}^N\) is the set of all subsets of size \(k_j\) of the set
\({1, 2, \dots, N}\).

\hypertarget{conditional-likelihoood-function}{%
\subsubsection{Conditional likelihoood
function}\label{conditional-likelihoood-function}}

The conditional likelihood function for all strata is written as
\begin{equation}
    \label{eq:conlikelihood}
    \begin{aligned}
    &   L(\mathbf{A}, h)  = \prod_{j=1}^M {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
    \end{aligned}
\end{equation}

\hypertarget{conditional-log-likelihood-function}{%
\subsubsection{Conditional log likelihood
function}\label{conditional-log-likelihood-function}}

The full conditional log likelihood function is the sum of the log
likelihoods for each stratum and can be written as

\begin{equation}
    \label{eq:condloglikelihood}
    \begin{aligned}
    &   \text{log}(L(\mathbf{A}, h))  = \sum_{j=1}^M \sum_{l \in O_j}\mathbf{A}[l, ] h  - \sum_{j=1}^M \text{log}\sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) 
    & = \sum_{j=1}^M \mathbf{A} h y_j  - \sum_{j=1}^M \text{log}\sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h )
    \end{aligned}
\end{equation}

\hypertarget{the-estimator}{%
\subsubsection{The Estimator}\label{the-estimator}}

The maximum likelihood estimator is then defined as \(\mathbf{A}\) which
maximize (\ref{eq:condloglikelihood}), which is equivalent to minimizing
the negative conditional log likelihood.

\hypertarget{miscellaneous}{%
\subsection{Miscellaneous}\label{miscellaneous}}

Constraints:

\begin{itemize}
\tightlist
\item
  Case \(\chi\): Here I imagine the constraints are on the Laplacian
\end{itemize}

\begin{equation}
\begin{aligned}
&\quad \text{tr}(L) = N, \\
&\quad L_{i,j} = L_{j,i} \leq 0, \phantom{..} i \neq j, \\
&\quad L\cdot \textbf{1} = \textbf{0} \\
\end{aligned}
\end{equation}

\begin{itemize}
\tightlist
\item
  Case with adjacency matrix:
\end{itemize}

\begin{equation}
\begin{aligned}
&\quad A_{i,j} = 0 \text{ if } i = j, \\
&\quad A_{i,j} = A_{j,i} \geq 0, \phantom{..} \text{ if } i \neq j
\end{aligned}
\end{equation}

\begin{itemize}
\tightlist
\item
  Consider the quadratic form \[
  x^TLx = \frac{1}{2}\sum_{(i,j)\in E}w_{i,j}(f(i) - f(j))^2
  \]
\end{itemize}

Because \(x\) is a binomial, this expression sums the weights of edeges
with incident nodes that have differing signal values. Suppose the graph
has a constant signal, then \(x^TLx = 0\). Suppose, we are in the worst
case when incident nodes for each edge have a different signal; in this
case \(x^TLx = \frac{1}{2}\sum_{(i,j) \in E}w_{i,j}\). Note, we can
bound \(x^TLx\) from below by \(\min{w_{i,j}}\) in the case were a
single edge has incident nodes with differing signals. We can use these
bounds to gauge the quality of model.

Sigmoid computation, Bound and Branch method of optimization

hint for factor analysis solution might be useful because there is
another object function varimax.

\url{https://conservancy.umn.edu/bitstream/handle/11299/95957/Choi_umn_0130E_11451.pdf?sequence=1\&isAllowed=y}

\url{https://web.stanford.edu/~boyd/papers/pdf/max_sum_sigmoids.pdf}

\begin{itemize}
\item
  complete separation do not exist. observable metric ?, it is a
  potential new topic to be able to identify whether complete separation
  exists. possible discuss it in the Discussion and future work.
\item
  While working on this one, you may also consider implementing our
  regressor paper.
\end{itemize}

\hypertarget{model-specification}{%
\subsection{Model Specification}\label{model-specification}}

\hypertarget{our-goal-is-to-estimate-the-graph-laplacian}{%
\subsection{Our goal is to estimate the Graph
Laplacian}\label{our-goal-is-to-estimate-the-graph-laplacian}}

\begin{itemize}
\tightlist
\item
  We do not have to use the eigenvector matrix \(\chi\). Instead, we may
  consider adjacency matrix \(A\) in place of \(\chi\). This is a viable
  direction.
\end{itemize}

Maximum Likelihood estimation, Quasi likelihood estimation,

\end{document}

### 2022-04-25 poster html copy/poster html.Rmd
Updated poster.

---
title: Graph Topology Learning from Binary Signals on Graph
author:
  - name: Skip Moses
    affil: 1
  - name: Jing Guo
    affil: 1
  - name: Robin Donatello
    affil: 1
affiliation:
  - num: 1
    address: Department of Mathematics and Statistics, California State University, Chico
column_numbers: 4
primary_colour: "#9D2235"
secondary_colour: "#FFFFFF"
poster_height: "36in"
poster_width: "60in"
# logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
# logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

Data often has  an underlying structure or geometry that can be modeled as a signal on the vertices of a weighted, undirected graph. Traditionally, the emphasis was on using a underlying graph, or network, to understand the properties of signals over the vertices. Recently, there has been a surge in converse problem; of learning a graph structure from a set of signals satisfying some constraints [@xia2021graph] [@dong2016learning] [ @ortega2018graph]. In previous research [@dong2016learning], [@tugnait2021sparse], [@pu2021learning], and [@saboksayr2021accelerated], signals on graph were assumed to follow multivariate gaussian distributions, but there has been little exploration in learning a network from binomial signals. In this work, we develop a noval methodology that allows for learning graph topology given a set of binary signals on the graph. An example of such signals on graph is presented in Figure 1.

![Figure 1. Binary Signals on Graph](pictures/gt_graph.png){width=90%}

# Methods

#### Signals on the graph and model specification
We consider a weighted undirected graph $G = (V, E)$, with the vertices set $V = {1, 2, \dots, N}$, and edge set $E$.  Let $\mathbf{A}$ denote the weighted adjacency matrix for the graph $G$. In the case of weighted undirected graph, $\mathbf{A}$ is a square and symmetric matrix.

Let $Y_{i,j}$ denote the signal on the node $i$ of graph $G$ at round $j$, where $j = 1, \dots, M$, and $i = 1, \dots, N$. We assume that $Y_{i,j}$ is a binary signal that can be 1, or 0.

Suppose the signals at stratum $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at stratum $k$ denoted by $Y[,k ]$, for $j \neq k$. Let $p_{i,j}$ denote the probability of $Y_{i,j} = 1$. Our model assumes

\begin{equation}
\label{eq: binaryglm}
\text{logit}(p_{i,j}) = \mathbf{A} h )_i,
\end{equation}

where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$ and assumed to be a standard normal random vector, and $\alpha_j$ is a round specific parameter at stratum $j$, and assumed to be normally distributed with mean of 0, and unknown variance $\sigma^2$.

#### Method of Estimation
##### Maximum likelihood for one stratum

Consider the proabability mass function for a given $A$ and signal $y = Y[,k]$
\begin{align}
P_{Ah}(y_i) &= P^{y_i}(1-p)^{1-y_i} \\
            &= \left(\frac{e^{A[i,]h^T}}{1 + e^{A[i,]h^T}}\right)\left(1- \frac{e^{A[i,]h^T}}{1 + e^{A[i,]h^T}}\right)^{1-y_i} \\
            &= \left(\frac{e^{A[i,]h^T}}{1 + e^{A[i,]h^T}}\right)\left(\frac{1}{1 + e^{A[i,]h^T}}\right)^{1-y_i} \\
            &= \frac{e^{y(A[i,]h^T)}}{1 + e^{A[i,]h^T}}                     
\end{align}

Therefore, our Likelihood function will be given by

\begin{align}
\mathcal{L}(h) = \prod_{i=1}^N\frac{e^{y_i(A[i,]h^T)}}{1 + e^{A[i,]h^T}} 
\end{align}

In order to maximize we consider the natural logarithm of our likelihood

\begin{align}
\log(\mathcal{L}(h)) = \sum_{i=1}^N\left(y_i(A[i,]h^T) - \log(1 + e^{A[i,]h^T})\right)
\end{align}

##### Optimization Program

Taking inspiration from the above derivation we will solve for estimated $A$ by maximizing the following

\begin{equation}
\label{eq:optimization}
\begin{aligned}
&\max_{A,h} \sum_{j = 1}^M\sum_{i=1}^N\left(y_{i,j}(A[i,]h^T) - \log(1 + e^{A[i,]h^T})\right) - \alpha \vert L \vert _ F \\
\textrm{s.t.} \quad  &A_{i,j} = 0 \text{ if } i =j\\
                     &A_{i,j} \geq 0 \text{ if } i \neq j\\
                     &\mathbb{1}h^T = 0 \\
                     &\max(h) \leq a \\
                     &\min(h) \geq b
\end{aligned}
\end{equation}
where $\alpha$ is a tunning parameter for controlling the sparsity and $a$ and $b$ are tunning parameters for restricting the spread of the values of $h$.

<hr /> 
<hr /> 
$\textbf{Algorithm 1:}$ Estimate $A$ given $Y$.
<hr /> 
<hr />

\begin{align*}
&1) \textbf{ Input: } \text{ Input a signal } Y.\\
&2) \textbf{ Output: } \text{ Output an estimated } A.\\
&3) \textbf{ Initialization: } h_{i,0} \sim \mathcal{N}(0,1) \text{ for } $i = 1,\ldots, N$\\
&4) \textbf{ for } t = 1, \ldots, iter:\\
&5) \textbf{ Update } A \textbf{ given } h:\\
&6) \textbf{        Update } h \textbf{ given } A:\\
&7) \textbf{ end for }
\end{align*}
<hr />

# Results

In each iteration of step 5) and 6) of Algorithm 1, the optimization program gives a Diciplined Concave Program that can be solved efficiently in Python with the CVXPY libarary. A random Erd\H{o}s-Reyni graph on $N = 20$ nodes and edge probability $p = 0.2$. Heat maps of the ground truth adjacency matrix and estitmated adjacency matrix are given, along with circular embeddings of the ground truth and estimated graphs.

Ground Truth               |  Estimation 
:-------------------------:|:-------------------------:
![](pictures/gt_A_heatmap.png){width=125%}  |  ![](pictures/est_A_heatmap.png){width=125%}

![Figure 2: Estimated Graph](pictures/est_graph.png){width=90%}

# Discussion

Currently, GSP frameworks such as ours have limitations making them only practical in experimental settings. For instance, these frameworks require the input to be the entire graph. This automatically puts a harsh limit on the size of the graphs that can be learned. Another related limitation, is the availability of the algorithms used to learn the laplacian. In @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn converges to a globally optimal solution in $O (1/k)$. A natural next step would be to apply fast proximal-gradient iterations our framework to overcome scalability issues.

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```
# References

### 2022-04-25 poster html copy/poster html.Rmd
Revision in Poster

@@
 Recently, there has been a surge in converse problem; of learning a graph structure from a set of signals satisfying some constraints [@xia2021graph] [@dong2016learning] [ @ortega2018graph].
-In previous research [@dong2016learning], [@tugnait2021sparse], [@pu2021learning], and [@saboksayr2021accelerated], signals on graph were assumed to follow multivariate gaussian distributions, but there has been little exploration in learning a network from binomial signals.
-In this work, we develop a noval methodology that allows for learning graph topology given a set of binary signals on the graph.
+In previous research [@dong2016learning], [@tugnait2021sparse], [@pu2021learning], and [@saboksayr2021accelerated], signals on graph were assumed to follow multivariate Gaussian distributions, but there has been little exploration in learning a network from binomial signals.
+In this work, we develop a novel methodology that allows for learning graph topology given a set of binary signals on the graph.
 An example of such signals on graph is presented in Figure 1.
@@
 \label{eq: binaryglm}
-\text{logit}(p_{i,j}) = \mathbf{A} h )_i,
+\text{logit}(p_{i,j}) = (\mathbf{A} h )_i,
 \end{equation}
 
-where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$ and assumed to be a standard normal random vector, and $\alpha_j$ is a round specific parameter at stratum $j$, and assumed to be normally distributed with mean of 0, and unknown variance $\sigma^2$.
+where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$ and assumed to be a standard normal random vector.
 
@@
 \begin{align}
-P_{Ah}(y_i) &= P^{y_i}(1-p)^{1-y_i} \\
-            &= \left(\frac{e^{A[i,]h^T}}{1 + e^{A[i,]h^T}}\right)\left(1- \frac{e^{A[i,]h^T}}{1 + e^{A[i,]h^T}}\right)^{1-y_i} \\
-            &= \left(\frac{e^{A[i,]h^T}}{1 + e^{A[i,]h^T}}\right)\left(\frac{1}{1 + e^{A[i,]h^T}}\right)^{1-y_i} \\
-            &= \frac{e^{y(A[i,]h^T)}}{1 + e^{A[i,]h^T}}                     
+P_{Ah}(y_i) &= p^{y_i}(1-p)^{1-y_i} \\
+            &= \left(\frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{y_i}\left(1- \frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{1-y_i} \\
+            &= \left(\frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{y_i}\left(\frac{1}{1 + e^{A[i,]h}}\right)^{1-y_i}   \\
+            &= \frac{e^{y_iA[i,]h}}{1 + e^{A[i,]h}}
+
 \end{align}
@@
 \begin{align}
-\mathcal{L}(h) = \prod_{i=1}^N\frac{e^{y_i(A[i,]h^T)}}{1 + e^{A[i,]h^T}} 
+\mathcal{L}(h) = \prod_{i=1}^N\left(\frac{e^{y_iA[i,]h}}{1 + e^{A[i,]h}}\right)
 \end{align}
@@
 \begin{align}
-\log(\mathcal{L}(h)) = \sum_{i=1}^N\left(y_i(A[i,]h^T) - \log(1 + e^{A[i,]h^T})\right)
+\log(\mathcal{L}(h)) = \sum_{i=1}^N\left(y_i(A[i,]h) - \log(1 + e^{A[i,]h})\right)
 \end{align}
@@
 \begin{aligned}
-&\max_{A,h} \sum_{j = 1}^M\sum_{i=1}^N\left(y_{i,j}(A[i,]h^T) - \log(1 + e^{A[i,]h^T})\right) - \alpha \vert L \vert _ F \\
+&\max_{A,h} \sum_{j = 1}^M\sum_{i=1}^N\left(y_{i,j}(A[i,]h) - \log(1 + e^{A[i,]h})\right) - \alpha \vert L \vert _ F \\
 \textrm{s.t.} \quad  &A_{i,j} = 0 \text{ if } i =j\\
@@
 \end{equation}
-where $\alpha$ is a tunning parameter for controlling the sparsity and $a$ and $b$ are tunning parameters for restricting the spread of the values of $h$.
+where $\alpha$ is a tuning parameter for controlling the sparsity and $a$ and $b$ are tuning parameters for restricting the spread of the values of $h$.
 
@@
 &2) \textbf{ Output: } \text{ Output an estimated } A.\\
-&3) \textbf{ Initialization: } h_{i,0} \sim \mathcal{N}(0,1) \text{ for } $i = 1,\ldots, N$\\
+&3) \textbf{ Initialization: } h_{i,0} \sim \mathcal{N}(0,1) \text{ for } i = 1,\ldots, N \\
 &4) \textbf{ for } t = 1, \ldots, iter:\\
@@
 
-In each iteration of step 5) and 6) of Algorithm 1, the optimization program gives a Diciplined Concave Program that can be solved efficiently in Python with the CVXPY libarary.
+In each iteration of step 5) and 6) of Algorithm 1, the optimization program gives a Disciplined Concave Program that can be solved efficiently in Python with the CVXPY library.
 A random Erd\H{o}s-Reyni graph on $N = 20$ nodes and edge probability $p = 0.2$.
-Heat maps of the ground truth adjacency matrix and estitmated adjacency matrix are given, along with circular embeddings of the ground truth and estimated graphs.
+Heat maps of the ground truth adjacency matrix and estimated adjacency matrix are given, along with circular embedding of the ground truth and estimated graphs.
 
@@
 ```
+# Acknowledgement
+This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
+
 # References

### 2022-04-26 poster html copy/poster html.Rmd
Updated final draft of poster.

@@
 
-Consider the proabability mass function for a given $A$ and signal $y = Y[,k]$
+Consider the probability mass function for a given $A$ and signal $y = Y[,k]$
 \begin{align}
@@
 
-Ground Truth               |  Estimation 
-:-------------------------:|:-------------------------:
-![](pictures/gt_A_heatmap.png){width=125%}  |  ![](pictures/est_A_heatmap.png){width=125%}
+##### Synthetic Data Generation
+
+To generate a single signal for a given adjacency matrix $A \in \mathbb{R}^{N\times N}$ and latent factor vector $h \in \mathbb{R}^N$ (each $h_i \sim \mathcal{N}(0,1)$), a vector of odds, $Ah$, is compared to a vector $T$, where $T_i$ selected uniformly at random for each $i = 1, \ldots , N$.
+If $T_k < Ah_k$, then node $k$ takes the signal value of $1$, and $0$ otherwise.
+We generate $M = 100$ synthetic signals, and use them to learn an adjacency matrix.
+The learned graph is found with parameter values $\alpha = .2$, $a = 1$ and $b = -1$.
+
+&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**Ground Truth** &nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**Learned**
+
+![](pictures/gt_A_heatmap.png){width=45%}  ![](pictures/est_A_heatmap.png){width=45%}
 

### 2022-04-27 poster html copy/poster html.Rmd
Poster update.

@@
   - name: Skip Moses
-    affil: 1
-  - name: Jing Guo
-    affil: 1
-  - name: Robin Donatello
-    affil: 1
 affiliation:
-  - num: 1
     address: Department of Mathematics and Statistics, California State University, Chico
@@
 
-![Figure 1. Binary Signals on Graph](pictures/gt_graph.png){width=90%}
+```{r GTG, echo=FALSE,out.width="90%", out.height="20%",fig.cap="Circular Embedding of ground truth graph",fig.show='hold',fig.align='center'}
+knitr::include_graphics(c("pictures/gt_graph.png"))
+```
 
@@
 Let $Y_{i,j}$ denote the signal on the node $i$ of graph $G$ at round $j$, where $j = 1, \dots, M$, and $i = 1, \dots, N$. We assume that $Y_{i,j}$ is a binary signal that can be 1, or 0. 
-
 Suppose the signals at stratum $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at stratum $k$ denoted by $Y[,k ]$, for $j \neq k$.
@@
 In each iteration of step 5) and 6) of Algorithm 1, the optimization program gives a Disciplined Concave Program that can be solved efficiently in Python with the CVXPY library.
-A random Erd\H{o}s-Reyni graph on $N = 20$ nodes and edge probability $p = 0.2$.
-Heat maps of the ground truth adjacency matrix and estimated adjacency matrix are given, along with circular embedding of the ground truth and estimated graphs.
+We use a random Erd&#337;s-Reyni graph on $N = 20$ nodes and edge probability $p = 0.2$.
+Each edge weight $w_i \sim \mathcal{U}(0,1)$.
 
@@
 
-&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**Ground Truth** &nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**Learned**
+Heat maps of the ground truth adjacency matrix and estimated adjacency matrix are given in Figure 2, along with circular embedding of the ground truth and estimated graphs in Figure 3.
 
-![](pictures/gt_A_heatmap.png){width=45%}  ![](pictures/est_A_heatmap.png){width=45%}
+```{r HM, echo=FALSE,out.width="49%", out.height="20%",fig.cap="(Left) A heatmap of the ground truth adjacency matrix.
+(Right) A heatmap of the estimated adjacency matrix.",fig.show='hold',fig.align='center'}
+knitr::include_graphics(c("pictures/gt_A_heatmap.png","pictures/est_A_heatmap.png"))
+```
 
-![Figure 2: Estimated Graph](pictures/est_graph.png){width=90%}
+```{r EAG, echo=FALSE,out.width="90%", out.height="20%",fig.cap="Circular Embedding of Estimated graph",fig.show='hold',fig.align='center'}
+knitr::include_graphics(c("pictures/est_graph.png"))
+```
 
@@
 
-Currently, GSP frameworks such as ours have limitations making them only practical in experimental settings.
-For instance, these frameworks require the input to be the entire graph.
-This automatically puts a harsh limit on the size of the graphs that can be learned.
-Another related limitation, is the availability of the algorithms used to learn the laplacian.
+Currently, GSP frameworks such as ours have limitations.
+For instance, these frameworks require the input to be set of complete signals.
+This limits the size of graphs that can be learned.
+Another related limitation, is the scalability of the algorithms used to learn a topology for the graph.
 In @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn converges to a globally optimal solution in $O (1/k)$.
@@
 This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
+This work would not have been possible without the guidence of Dr.
+Jing Guo.
+I am extremely grateful for all of meetings over the semester.
 

### 2022-04-27 poster html copy/poster html.Rmd
poster update.

@@
 
-```{r GTG, echo=FALSE,out.width="90%", out.height="20%",fig.cap="Circular Embedding of ground truth graph",fig.show='hold',fig.align='center'}
+```{r GTG, echo=FALSE,out.width="80%", out.height="20%",fig.cap="Circular Embedding of ground truth graph",fig.show='hold',fig.align='center'}
 knitr::include_graphics(c("pictures/gt_graph.png"))
@@
 
-<hr /> 
-<hr /> 
 $\textbf{Algorithm 1:}$ Estimate $A$ given $Y$.
-<hr /> 
-<hr />
 
@@
 The learned graph is found with parameter values $\alpha = .2$, $a = 1$ and $b = -1$.
-
 Heat maps of the ground truth adjacency matrix and estimated adjacency matrix are given in Figure 2, along with circular embedding of the ground truth and estimated graphs in Figure 3.
@@
 
-```{r EAG, echo=FALSE,out.width="90%", out.height="20%",fig.cap="Circular Embedding of Estimated graph",fig.show='hold',fig.align='center'}
+```{r EAG, echo=FALSE,out.width="80%", out.height="20%",fig.cap="Circular Embedding of Estimated graph",fig.show='hold',fig.align='center'}
 knitr::include_graphics(c("pictures/est_graph.png"))
 ``` 
-
 # Discussion
-
-Currently, GSP frameworks such as ours have limitations.
-For instance, these frameworks require the input to be set of complete signals.
+One shortcoming of this framework is it requires the input to be a complete set of signals.
 This limits the size of graphs that can be learned.
-Another related limitation, is the scalability of the algorithms used to learn a topology for the graph.
+Another, is the scalability of the algorithms used to learn a topology for the graph.
 In @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn converges to a globally optimal solution in $O (1/k)$.
@@
 This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
+Thank you Dr.
+Robin Donatello for approving this project.
 This work would not have been possible without the guidence of Dr.

### 2022-04-27 poster html copy/poster html.Rmd
Poster updates

--- 2022-04-26 poster html copy/poster html.Rmd
@@
   - name: Skip Moses
-    affil: 1
   - name: Jing Guo
-    affil: 1
   - name: Robin Donatello
-    affil: 1
 affiliation:
-  - num: 1
     address: Department of Mathematics and Statistics, California State University, Chico
@@
 poster_width: "60in"
-# logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
+# logoright_name: 
 # logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
@@
 Traditionally, the emphasis was on using a underlying graph, or network, to understand the properties of signals over the vertices.
-Recently, there has been a surge in converse problem; of learning a graph structure from a set of signals satisfying some constraints [@xia2021graph] [@dong2016learning] [ @ortega2018graph].
+Recently, there has been a surge in converse problem; learning a graph structure from a set of signals satisfying some constraints [@xia2021graph] [@dong2016learning] [ @ortega2018graph].
 In previous research [@dong2016learning], [@tugnait2021sparse], [@pu2021learning], and [@saboksayr2021accelerated], signals on graph were assumed to follow multivariate Gaussian distributions, but there has been little exploration in learning a network from binomial signals.
 In this work, we develop a novel methodology that allows for learning graph topology given a set of binary signals on the graph.
-An example of such signals on graph is presented in Figure 1.
 
-![Figure 1. Binary Signals on Graph](pictures/gt_graph.png){width=90%}
+```{r GTG, echo=FALSE,out.width="80%", out.height="20%",fig.cap="Circular Embedding of random Erd&#337;s-Reyni Graph with edge probability p = 0.2.
+Each edge weight follows uniform random distribution on (0,1).
+Grey nodes indicate a signal value of 0 and black nodes indicate a signal value of 1.",fig.show='hold',fig.align='center'}
+knitr::include_graphics(c("pictures/gt_graph.png"))
+```
 
@@
 We consider a weighted undirected graph $G = (V, E)$, with the vertices set $V = {1, 2, \dots, N}$, and edge set $E$.
-Let $\mathbf{A}$ denote the weighted adjacency matrix for the graph $G$.
+Let $\mathbf{A}$ denote the weighted adjacency matrix of $G$.
 In the case of weighted undirected graph, $\mathbf{A}$ is a square and symmetric matrix.
 
-Let $Y_{i,j}$ denote the signal on the node $i$ of graph $G$ at round $j$, where $j = 1, \dots, M$, and $i = 1, \dots, N$. We assume that $Y_{i,j}$ is a binary signal that can be 1, or 0.
-
-Suppose the signals at stratum $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at stratum $k$ denoted by $Y[,k ]$, for $j \neq k$.
-Let $p_{i,j}$ denote the probability of $Y_{i,j} = 1$.
+Let $\mathbf{Y}_{i,j}$ denote the signal on the node $i$ of graph $G$ at round $j$, where $j = 1, \dots, M$, and $i = 1, \dots, N$.
+We assume that $\mathbf{Y}_{i,j}$ is a binary signal that can be 1, or 0.
+Suppose the signals at stratum $j$ denoted by $\mathbf{Y}[, j]$ for all $N$ nodes are independent of the signals at stratum $k$ denoted by $\mathbf{Y}[,k ]$, for $j \neq k$.
+Let $p_{i,j}$ denote the probability of $\mathbf{Y}_{i,j} = 1$.
 Our model assumes
@@
 
-#### Method of Estimation
 ##### Maximum likelihood for one stratum
 
-Consider the probability mass function for a given $A$ and signal $y = Y[,k]$
+Consider the probability mass function for a given $\mathbf{A}$ and signal $y = \mathbf{Y}[,k]$
 \begin{align}
-P_{Ah}(y_i) &= p^{y_i}(1-p)^{1-y_i} \\
-            &= \left(\frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{y_i}\left(1- \frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{1-y_i} \\
-            &= \left(\frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{y_i}\left(\frac{1}{1 + e^{A[i,]h}}\right)^{1-y_i}   \\
-            &= \frac{e^{y_iA[i,]h}}{1 + e^{A[i,]h}}
+P_{\mathbf{A}h}(y_i) &= p^{y_i}(1-p)^{1-y_i} \\
+            &= \left(\frac{e^{\mathbf{A}[i,]h}}{1 + e^{\mathbf{A}[i,]h}}\right)^{y_i}\left(1- \frac{e^{\mathbf{A}[i,]h}}{1 + e^{\mathbf{A}[i,]h}}\right)^{1-y_i} \\
+            &= \left(\frac{e^{\mathbf{A}[i,]h}}{1 + e^{\mathbf{A}[i,]h}}\right)^{y_i}\left(\frac{1}{1 + e^{\mathbf{A}[i,]h}}\right)^{1-y_i}   \\
+            &= \frac{e^{y_i\mathbf{A}[i,]h}}{1 + e^{\mathbf{A}[i,]h}}
 
@@
 \begin{align}
-\mathcal{L}(h) = \prod_{i=1}^N\left(\frac{e^{y_iA[i,]h}}{1 + e^{A[i,]h}}\right)
+\mathcal{L}(h) = \prod_{i=1}^N\left(\frac{e^{y_i\mathbf{A}[i,]h}}{1 + e^{\mathbf{A}[i,]h}}\right)
 \end{align}
@@
 \begin{align}
-\log(\mathcal{L}(h)) = \sum_{i=1}^N\left(y_i(A[i,]h) - \log(1 + e^{A[i,]h})\right)
+\log(\mathcal{L}(h)) = \sum_{i=1}^N\left(y_i(\mathbf{A}[i,]h) - \log(1 + e^{\mathbf{A}[i,]h})\right)
 \end{align}
@@
 
-Taking inspiration from the above derivation we will solve for estimated $A$ by maximizing the following
+Taking inspiration from the above derivation we will solve for estimated $\mathbf{A}$ by maximizing the following
 
@@
 \begin{aligned}
-&\max_{A,h} \sum_{j = 1}^M\sum_{i=1}^N\left(y_{i,j}(A[i,]h) - \log(1 + e^{A[i,]h})\right) - \alpha \vert L \vert _ F \\
-\textrm{s.t.} \quad  &A_{i,j} = 0 \text{ if } i =j\\
-                     &A_{i,j} \geq 0 \text{ if } i \neq j\\
-                     &\mathbb{1}h^T = 0 \\
-                     &\max(h) \leq a \\
-                     &\min(h) \geq b
+&\max_{\mathbf{A},h} \sum_{j = 1}^M\sum_{i=1}^N\left(y_{i,j}(\mathbf{A}[i,]h) - \log(1 + e^{\mathbf{A}[i,]h})\right) - \alpha \vert L \vert _ F \\
+\textrm{s.t.} \quad  &\mathbf{A}_{i,j} = 0 \text{ if } i =j;\,\, \mathbf{A}_{i,j} \geq 0 \text{ if } i \neq j\\
+                     &\max(h) \leq a ;  \,\, \min(h) \geq b \,\, \mathbb{1}h^T = 0  
 \end{aligned}
 \end{equation}
-where $\alpha$ is a tuning parameter for controlling the sparsity and $a$ and $b$ are tuning parameters for restricting the spread of the values of $h$.
-
+where $\alpha$ is a tuning parameter for controlling the sparsity and $\mathbf{A}$ and $b$ are tuning parameters for restricting the spread of the values of $h$. 
 <hr />
-<hr /> 
-$\textbf{Algorithm 1:}$ Estimate $A$ given $Y$.
-<hr /> 
-<hr />
-
 \begin{align*}
-&1) \textbf{ Input: } \text{ Input a signal } Y.\\
-&2) \textbf{ Output: } \text{ Output an estimated } A.\\
+&\textbf{Algorithm: Binary Signal Representation} \\
+&1) \textbf{ Input: } \text{ Input a signal } \mathbf{Y}.\\
+&2) \textbf{ Output: } \text{ Output an estimated } \mathbf{A}.\\
 &3) \textbf{ Initialization: } h_{i,0} \sim \mathcal{N}(0,1) \text{ for } i = 1,\ldots, N \\
 &4) \textbf{ for } t = 1, \ldots, iter:\\
-&5) \textbf{ Update } A \textbf{ given } h:\\
-&6) \textbf{        Update } h \textbf{ given } A:\\
-&7) \textbf{ end for }
+&5) \textbf{ Update } \mathbf{A} \textbf{ given } h:\\
+&6) \,\,\,\, \textit{ Fix h in Optimization Program and solve \mathbf{A}} \\
+&7) \textbf{        Update } h \textbf{ given } \mathbf{A}:\\
+&8) \,\,\,\, \textit{ Fix } \mathbf{A} \text{ in Optimization Program and solve h} \\
+&9) \textbf{ end for }
 \end{align*}
@@
 In each iteration of step 5) and 6) of Algorithm 1, the optimization program gives a Disciplined Concave Program that can be solved efficiently in Python with the CVXPY library.
-A random Erd\H{o}s-Reyni graph on $N = 20$ nodes and edge probability $p = 0.2$.
-Heat maps of the ground truth adjacency matrix and estimated adjacency matrix are given, along with circular embedding of the ground truth and estimated graphs.
 
@@
 
-To generate a single signal for a given adjacency matrix $A \in \mathbb{R}^{N\times N}$ and latent factor vector $h \in \mathbb{R}^N$ (each $h_i \sim \mathcal{N}(0,1)$), a vector of odds, $Ah$, is compared to a vector $T$, where $T_i$ selected uniformly at random for each $i = 1, \ldots , N$.
-If $T_k < Ah_k$, then node $k$ takes the signal value of $1$, and $0$ otherwise.
+Let $\mathbf{A}$ be the adjacency matrix of the graph in Figure \@ref(fig:GTG), and $h \in \mathbb{R}$ be such that $h_i \sim \mathcal{N}(0,1)$.
+Set $p = \mathbf{A}h$, and compare this to a vector $t$, where each $t_i$ follows a random uniform distribution $\mathcal{U}(0,1)$.
+If $t_k < p_k$, then node $k$ takes the signal value of $1$, and $0$ otherwise.
 We generate $M = 100$ synthetic signals, and use them to learn an adjacency matrix.
@@
 
-&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**Ground Truth** &nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**Learned**
+##### Graph Learning Results
 
-![](pictures/gt_A_heatmap.png){width=45%}  ![](pictures/est_A_heatmap.png){width=45%}
+```{r HM, echo=FALSE,out.width="49%", out.height="20%",fig.cap="(Left) A heatmap of the ground truth adjacency matrix.
+(Right) A heatmap of the estimated adjacency matrix.
+We can see the learned adjacency matrix shares some similar features to the ground truth, but the learned adjacency matrix is sparser than the ground truth.",fig.show='hold',fig.align='center'}
+knitr::include_graphics(c("pictures/gt_A_heatmap.png","pictures/est_A_heatmap.png"))
+```
 
-![Figure 2: Estimated Graph](pictures/est_graph.png){width=90%}
-
+```{r EAG, echo=FALSE,out.width="80%", out.height="20%",fig.cap="Circular Embedding of Estimated graph.
+Note the overall weight of each edge is smaller than the edge weights of the ground truth.",fig.show='hold',fig.align='center'}
+knitr::include_graphics(c("pictures/est_graph.png"))
+``` 
 # Discussion
 
-Currently, GSP frameworks such as ours have limitations making them only practical in experimental settings.
-For instance, these frameworks require the input to be the entire graph.
-This automatically puts a harsh limit on the size of the graphs that can be learned.
-Another related limitation, is the availability of the algorithms used to learn the laplacian.
-In @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn converges to a globally optimal solution in $O (1/k)$.
-A natural next step would be to apply fast proximal-gradient iterations our framework to overcome scalability issues.
+To our knowledge, this is the first work on learning graph topology from binary signals.
+We have developed a method to effectively learn the graph adjacency matrix from binary signals.
+This model can be easily extended for learning binomial signals in general.
+Incorporating parameter optimization techniques would be a natural improvement on this model.
+Moreover, it would be desirable to develop scalable algorithms that can be used to learn a topology for a large graph from signals.
+Recently, in @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn improving the over-all runtime.
 

### 2022-04-27 poster html copy/poster html.Rmd
Poster updates

@@
   - name: Jing Guo
-  - name: Robin Donatello
 affiliation:
@@
 # Acknowledgement
-This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
+This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you to Robin Donatello for approving this work.
 

### 2022-04-27 poster html copy/poster html.Rmd
poster update

@@
 poster_width: "60in"
-# logoright_name: 
+logoright_name: Chico-State-Flame-Cardinal300dpi.png
 # logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png

### 2022-04-28 poster html copy/poster html.Rmd
minor changes on the poster

@@
 Traditionally, the emphasis was on using a underlying graph, or network, to understand the properties of signals over the vertices.
-Recently, there has been a surge in converse problem; learning a graph structure from a set of signals satisfying some constraints [@xia2021graph] [@dong2016learning] [ @ortega2018graph].
-In previous research [@dong2016learning], [@tugnait2021sparse], [@pu2021learning], and [@saboksayr2021accelerated], signals on graph were assumed to follow multivariate Gaussian distributions, but there has been little exploration in learning a network from binomial signals.
-In this work, we develop a novel methodology that allows for learning graph topology given a set of binary signals on the graph.
+Recently, there has been a surge in converse problem; learning a graph structure from a set of signals satisfying some constraints [@dong2016learning] [ @ortega2018graph].
+In previous research [@dong2016learning], [@tugnait2021sparse], and [@saboksayr2021accelerated], signals on graph were assumed to follow multivariate Gaussian distributions, but there has been little exploration in learning a network from binomial signals.
+In this work, we develop a novel methodology that allows for learning graph topology given a set of binary signals on the graph as shown in Figure \@ref(fig:GTG).
 
-```{r GTG, echo=FALSE,out.width="80%", out.height="20%",fig.cap="Circular Embedding of random Erd&#337;s-Reyni Graph with edge probability p = 0.2.
+```{r GTG, echo=FALSE,out.width="90%", out.height="25%",fig.cap="Circular Embedding of random Erd&#337;s-Reyni Graph with edge probability p = 0.2.
 Each edge weight follows uniform random distribution on (0,1).
@@
 \textrm{s.t.} \quad  &\mathbf{A}_{i,j} = 0 \text{ if } i =j;\,\, \mathbf{A}_{i,j} \geq 0 \text{ if } i \neq j\\
-                     &\max(h) \leq a ;  \,\, \min(h) \geq b \,\, \mathbb{1}h^T = 0  
+                     &\max(h) \leq a ;  \,\, \min(h) \geq b \,\, ; \mathbb{1}h^T = 0  
 \end{aligned}
@@
 where $\alpha$ is a tuning parameter for controlling the sparsity and $\mathbf{A}$ and $b$ are tuning parameters for restricting the spread of the values of $h$.
+
+We presented our optimization algorithm below.
+In each iteration of step 5) and 6) of Algorithm 1, the optimization program gives a Disciplined Concave Program that can be solved efficiently in Python with the CVXPY library.
+
 <hr />
 \begin{align*}
-&\textbf{Algorithm: Binary Signal Representation} \\
+&\textbf{Algorithm 1: Binary Signal Graph Learning} \\
 &1) \textbf{ Input: } \text{ Input a signal } \mathbf{Y}.\\
@@
 &5) \textbf{ Update } \mathbf{A} \textbf{ given } h:\\
-&6) \,\,\,\, \textit{ Fix h in Optimization Program and solve \mathbf{A}} \\
+&6) \,\,\,\, \textit{ Fix }  h \textit{ in Optimization Program and solve } \mathbf{A} \\
 &7) \textbf{        Update } h \textbf{ given } \mathbf{A}:\\
@@
 # Results
-
-In each iteration of step 5) and 6) of Algorithm 1, the optimization program gives a Disciplined Concave Program that can be solved efficiently in Python with the CVXPY library.
-
 ##### Synthetic Data Generation
-
 Let $\mathbf{A}$ be the adjacency matrix of the graph in Figure \@ref(fig:GTG), and $h \in \mathbb{R}$ be such that $h_i \sim \mathcal{N}(0,1)$.
-Set $p = \mathbf{A}h$, and compare this to a vector $t$, where each $t_i$ follows a random uniform distribution $\mathcal{U}(0,1)$.
+Set $p$ as a logistic function of $\mathbf{A}h$, and compare $p$ to a vector $t$, where each $t_i$ follows a random uniform distribution $\mathcal{U}(0,1)$.
 If $t_k < p_k$, then node $k$ takes the signal value of $1$, and $0$ otherwise.
 We generate $M = 100$ synthetic signals, and use them to learn an adjacency matrix.
-The learned graph is found with parameter values $\alpha = .2$, $a = 1$ and $b = -1$.
 
@@
 
+The learned graph is found with parameter values $\alpha = .2$, $a = 1$ and $b = -1$ by implementing Algorithm 1.
+We can see the learned adjacency matrix shares some similar features to the ground truth (Figure \@ref(fig:HM)), but the learned adjacency matrix is sparser than the ground truth (Figure \@ref(fig:HM) and Figure \@ref(fig:EAG)).
+
 ```{r HM, echo=FALSE,out.width="49%", out.height="20%",fig.cap="(Left) A heatmap of the ground truth adjacency matrix.
 (Right) A heatmap of the estimated adjacency matrix.
-We can see the learned adjacency matrix shares some similar features to the ground truth, but the learned adjacency matrix is sparser than the ground truth.",fig.show='hold',fig.align='center'}
+",fig.show='hold',fig.align='center'}
 knitr::include_graphics(c("pictures/gt_A_heatmap.png","pictures/est_A_heatmap.png"))
@@
 
-```{r EAG, echo=FALSE,out.width="80%", out.height="20%",fig.cap="Circular Embedding of Estimated graph.
+```{r EAG, echo=FALSE,out.width="60%", out.height="10%",fig.cap="Circular Embedding of Estimated graph.
 Note the overall weight of each edge is smaller than the edge weights of the ground truth.",fig.show='hold',fig.align='center'}
@@
 # Discussion
-
 To our knowledge, this is the first work on learning graph topology from binary signals.
@@
 # Acknowledgement
-This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you to Robin Donatello for approving this work.
+This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
+Thank you to Robin Donatello for approving this work for Data Science Capstone Project.
 

### 2022-04-28 poster html copy/poster html.Rmd
Updated logos.

@@
 poster_width: "60in"
-logoright_name: Chico-State-Flame-Cardinal300dpi.png
-# logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
+logoright_name: pictures/DSI_Hexbin_sticker_01.png
+#logoright_name: pictures/logo1.png
 output: 
@@
 
-```{r GTG, echo=FALSE,out.width="90%", out.height="25%",fig.cap="Circular Embedding of random Erd&#337;s-Reyni Graph with edge probability p = 0.2.
+```{r GTG, echo=FALSE,out.width="80%", out.height="25%",fig.cap="Circular Embedding of random Erd&#337;s-Reyni Graph with edge probability p = 0.2.
 Each edge weight follows uniform random distribution on (0,1).
@@
 
-```{r EAG, echo=FALSE,out.width="60%", out.height="10%",fig.cap="Circular Embedding of Estimated graph.
+```{r EAG, echo=FALSE,out.width="80%", out.height="25%",fig.cap="Circular Embedding of Estimated graph.
 Note the overall weight of each edge is smaller than the edge weights of the ground truth.",fig.show='hold',fig.align='center'}
@@
 # Acknowledgement
-This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
-Thank you to Robin Donatello for approving this work for Data Science Capstone Project.
+
+ <body>      
+        <p style="color:black;font-size:24px;">This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
+Thank you to Robin Donatello for approving this work for Data Science Capstone Project.</p>
+</body>
+
+```{r , echo=FALSE,out.width="60%", out.height="10%",fig.show='hold',fig.align='center'}
+knitr::include_graphics(c("pictures/logo1.png"))
+```
 

### 2022-04-29 poster html copy/poster html.Rmd
fix logo

@@
 logoright_name: pictures/DSI_Hexbin_sticker_01.png
-#logoright_name: pictures/logo1.png
+logoleft_name: pictures/logo1.png
 output: 
@@
 ```
+<style>
+.poster_title {
+  width: 50%;
+  text-align: center;
+  float: left;
+  align-items: center;
+  justify-content: center;
+  padding: 30px;
+  margin-top: 0.1in;
+  margin-bottom: 0.1in;
+}
+
+.logo_left {
+  width: 30%;
+  display: flex;
+  align-items: center;
+  justify-content: center;
+}
+
+.logo_right {
+  width: 9%;
+  display: flex;
+  align-items: center;
+  justify-content: center;
+}
+
+</style>
 
@@
 Traditionally, the emphasis was on using a underlying graph, or network, to understand the properties of signals over the vertices.
-Recently, there has been a surge in converse problem; learning a graph structure from a set of signals satisfying some constraints [@dong2016learning] [ @ortega2018graph].
+Recently, there has been a surge in converse problem: learning a graph structure from a set of signals satisfying some constraints [@dong2016learning] [ @ortega2018graph].
 In previous research [@dong2016learning], [@tugnait2021sparse], and [@saboksayr2021accelerated], signals on graph were assumed to follow multivariate Gaussian distributions, but there has been little exploration in learning a network from binomial signals.
@@
  <body>      
-        <p style="color:black;font-size:24px;">This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
+        <p style="color:black;font-size:32px;">This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
 Thank you to Robin Donatello for approving this work for Data Science Capstone Project.</p>
@@
 
-```{r , echo=FALSE,out.width="60%", out.height="10%",fig.show='hold',fig.align='center'}
-knitr::include_graphics(c("pictures/logo1.png"))
-```
-
 # References

### 2022-04-30 poster html copy/poster html.Rmd
GSP Regressor Results.

@@
   - name: Skip Moses
-  - name: Jing Guo
+  - name: Dr. Jing Guo, Ph.D.
 affiliation:
@@
         <p style="color:black;font-size:32px;">This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
-Thank you to Robin Donatello for approving this work for Data Science Capstone Project.</p>
+Thank you to Dr.
+Robin Donatello, Ph.D., for approving this work for Data Science Capstone Project.</p>
 </body>

### 2022-04-30 Scripts/gl_sig_rep/Metrics.py

@@ -1,0 +1,72 @@
+import numpy as np
+import cvxpy as cp
+import matplotlib.pyplot as plt
+from scipy import sparse
+from pygsp import graphs, filters
+from numpy.linalg import inv
+import itertools as it
+
+# Count the edges given a threshhold
+def count_edges(Lap, threshhold):
+    count = 0
+    size = Lap.shape[0]
+    for i in range(0,size):
+        for j in range(0,i):
+            if abs(Lap[i][j]) > threshhold:
+                count = count + 1
+    if count > 0:
+        return(count)
+    else:
+        return(-1)
+
+def detect_edges(L1, L2, threshhold):
+    count = 0
+    size = L1.shape[0]
+    for i in range(0,size):
+        for j in range(0,i):
+            if (abs(L1[i][j]) > threshhold) and L2[i][j] < 0 and abs(L2[i][j]) > threshhold:
+                count = count + 1
+    return(count)
+
+# Count the number of edges two laplacians have in common. 
+# Computes the difference and counts the number of components
+# sufficiently close to 0.
+def compare_edges_strict(L1, L2):
+    Dif = abs(L1 - L2)
+    size = Dif.shape[0]
+    count = 0
+    for i in range(0,size):
+        for j in range(0,i):
+            if Dif[i][j] < .005:
+                count = count + 1
+    return(count)
+
+# Computes the proportion of correct edges in the Learned Laplacian
+def Precision(EstL, GTL, threshhold):
+    return(detect_edges(EstL, GTL, threshhold)/count_edges(EstL, threshhold))
+
+# Computes the proportion edges in Ground truth Laplacian 
+# that appear in learned Laplacian
+def Recall(EstL, GTL, threshhold):
+    return(detect_edges(EstL, GTL, threshhold)/count_edges(GTL, threshhold))
+
+def F_Measure(EstL, GTL, threshhold):
+    P = Precision(EstL, GTL, threshhold)
+    R = Recall(EstL, GTL, threshhold)
+    if P+R > 0:
+        return(2*((P*R)/(P+R)))
+    else:
+        return(-1)
+
+def Relative_Error(L1, L2):
+    return(np.linalg.norm(L1 - L2)/np.linalg.norm(L1))
+
+def SSE(L1, L2):
+    return(Relative_Error(L1,L2)**2)
+
+def ComputeMetrics(EstL, GTL, threshhold):
[…]

### 2022-04-30 Scripts/gl_sig_rep/Metrics.py
Most recent GSPRegressor file.

@@ -24,7 +24,7 @@ def detect_edges(L1, L2, threshhold):
     size = L1.shape[0]
     for i in range(0,size):
         for j in range(0,i):
-            if (abs(L1[i][j]) > threshhold) and L2[i][j] < 0 and abs(L2[i][j]) > threshhold:
+            if (abs(L1[i][j]) > threshhold) and L2[i][j] < 0:
                 count = count + 1
     return(count)
 

### 2022-05-12 Documents/paper/draft.Rmd
File managment for final submission.

--- 2022-03-13 draft.Rmd
@@
 date: "3/12/2022"
-output: html_document
+output:
+  pdf_document: default
+  html_document:
+    df_print: paged
+cls: IEEEtran.cls
 bibliography: ref.bib
-cls: IEEEtran.cls
 ---
@@
 This makes \ref{eq:quadraticform} well suited for measuring the smoothness of a signal on a graph.
-We can cast the problem of learning a graph by the optimization problem found in \cite{kalofolias2016learn}
+We can cast the problem of learning a graph by the optimization problem found in @kalofolias2016learn
 \begin{equation}
-	\label{eq:GLP}
 	\begin{aligned}
@@
 \end{equation}
+
+# Methods
+
+#### Signals on the graph and model specification
+We consider a weighted undirected graph $G = (V, E)$, with the vertices set $V = {1, 2, \dots, N}$, and edge set $E$.
+Let $\mathbf{A}$ denote the weighted adjacency matrix of $G$.
+In the case of weighted undirected graph, $\mathbf{A}$ is a square and symmetric matrix.
+
+Let $\mathbf{Y}_{i,j}$ denote the signal on the node $i$ of graph $G$ at round $j$, where $j = 1, \dots, M$, and $i = 1, \dots, N$.
+We assume that $\mathbf{Y}_{i,j}$ is a binary signal that can be 1, or 0.
+Suppose the signals at stratum $j$ denoted by $\mathbf{Y}[, j]$ for all $N$ nodes are independent of the signals at stratum $k$ denoted by $\mathbf{Y}[,k ]$, for $j \neq k$.
+Let $p_{i,j}$ denote the probability of $\mathbf{Y}_{i,j} = 1$.
+Our model assumes
+
+\begin{equation}
+\label{eq: binaryglm}
+\text{logit}(p_{i,j}) = (\mathbf{A} h )_i,
+\end{equation}
+
+where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$ and assumed to be a standard normal random vector.
+
+##### Maximum likelihood for one stratum
+
+Consider the probability mass function for a given $\mathbf{A}$ and signal $y = \mathbf{Y}[,k]$
+\begin{align}
+P_{\mathbf{A}h}(y_i) &= p^{y_i}(1-p)^{1-y_i} \\
+            &= \left(\frac{e^{\mathbf{A}[i,]h}}{1 + e^{\mathbf{A}[i,]h}}\right)^{y_i}\left(1- \frac{e^{\mathbf{A}[i,]h}}{1 + e^{\mathbf{A}[i,]h}}\right)^{1-y_i} \\
+            &= \left(\frac{e^{\mathbf{A}[i,]h}}{1 + e^{\mathbf{A}[i,]h}}\right)^{y_i}\left(\frac{1}{1 + e^{\mathbf{A}[i,]h}}\right)^{1-y_i}   \\
+            &= \frac{e^{y_i\mathbf{A}[i,]h}}{1 + e^{\mathbf{A}[i,]h}}
+\end{align}
+
+Therefore, our Likelihood function will be given by
+
+\begin{align}
+\mathcal{L}(h) = \prod_{i=1}^N\left(\frac{e^{y_i\mathbf{A}[i,]h}}{1 + e^{\mathbf{A}[i,]h}}\right)
+\end{align}
+
+In order to maximize we consider the natural logarithm of our likelihood
+
+\begin{align}
+\log(\mathcal{L}(h)) = \sum_{i=1}^N\left(y_i(\mathbf{A}[i,]h) - \log(1 + e^{\mathbf{A}[i,]h})\right)
+\end{align}
+
+##### Optimization Program
+
+Taking inspiration from the above derivation we will solve for estimated $\mathbf{A}$ by maximizing the following
+
+\begin{equation}
+\label{eq:optimization}
+\begin{aligned}
+&\max_{\mathbf{A},h} \sum_{j = 1}^M\sum_{i=1}^N\left(y_{i,j}(\mathbf{A}[i,]h) - \log(1 + e^{\mathbf{A}[i,]h})\right) - \alpha \vert L \vert _ F \\
+\textrm{s.t.} \quad  &\mathbf{A}_{i,j} = 0 \text{ if } i =j;\,\, \mathbf{A}_{i,j} \geq 0 \text{ if } i \neq j\\
+                     &\max(h) \leq a ;  \,\, \min(h) \geq b \,\, ; \mathbb{1}h^T = 0  
+\end{aligned}
+\end{equation}
+where $\alpha$ is a tuning parameter for controlling the sparsity and $\mathbf{A}$ and $b$ are tuning parameters for restricting the spread of the values of $h$.
+
+We presented our optimization algorithm below.
+In each iteration of step 5) and 6) of Algorithm 1, the optimization program gives a Disciplined Concave Program that can be solved efficiently in Python with the CVXPY library.
+
+<hr />
+\begin{align*}
+&\textbf{Algorithm 1: Binary Signal Graph Learning} \\
+&1) \textbf{ Input: } \text{ Input a signal } \mathbf{Y}.\\
+&2) \textbf{ Output: } \text{ Output an estimated } \mathbf{A}.\\
+&3) \textbf{ Initialization: } h_{i,0} \sim \mathcal{N}(0,1) \text{ for } i = 1,\ldots, N \\
+&4) \textbf{ for } t = 1, \ldots, iter:\\
+&5) \textbf{ Update } \mathbf{A} \textbf{ given } h:\\
+&6) \,\,\,\, \textit{ Fix }  h \textit{ in Optimization Program and solve } \mathbf{A} \\
+&7) \textbf{        Update } h \textbf{ given } \mathbf{A}:\\
+&8) \,\,\,\, \textit{ Fix } \mathbf{A} \text{ in Optimization Program and solve h} \\
+&9) \textbf{ end for }
+\end{align*}
+<hr /> 
+\newpage
+# Results
+### Synthetic Data Generation
+
+```{r GTG, echo=FALSE,out.width="80%", out.height="25%",fig.cap ="The ground truth graph with an example signal shown.",fig.show='hold',fig.align='center'}
+knitr::include_graphics(c("pictures/gt_graph.png"))
+```
+
+Let $\mathbf{A}$ be the adjacency matrix of the graph in Figure \@ref(fig:GTG), and $h \in \mathbb{R}$ be such that $h_i \sim \mathcal{N}(0,1)$.
+Set $p$ as a logistic function of $\mathbf{A}h$, and compare $p$ to a vector $t$, where each $t_i$ follows a random uniform distribution $\mathcal{U}(0,1)$.
+If $t_k < p_k$, then node $k$ takes the signal value of $1$, and $0$ otherwise.
+We generate $M = 100$ synthetic signals, and use them to learn an adjacency matrix.
+
+### Graph Learning Results
+
+The learned graph is found with parameter values $\alpha = .2$, $a = 1$ and $b = -1$ by implementing Algorithm 1.
+We can see the learned adjacency matrix shares some similar features to the ground truth (left), but the learned adjacency matrix is sparser than the ground truth (right).
+
+```{r HM, echo=FALSE,out.width="49%", out.height="20%",fig.cap="(Left) A heatmap of the ground truth adjacency matrix.
+(Right) A heatmap of the estimated adjacency matrix.
+",fig.show='hold',fig.align='center'}
+knitr::include_graphics(c("pictures/gt_A_heatmap.png","pictures/est_A_heatmap.png"))
+```
+
+```{r EAG, echo=FALSE,out.width="80%", out.height="25%",fig.cap="Circular Embedding of Estimated graph.
+Note the overall weight of each edge is smaller than the edge weights of the ground truth.",fig.show='hold',fig.align='center'}
+knitr::include_graphics(c("pictures/est_graph.png"))
+``` 
+# Discussion
+To our knowledge, this is the first work on learning graph topology from binary signals.
+We have developed a method to effectively learn the graph adjacency matrix from binary signals.
+This model can be easily extended for learning binomial signals in general.
+Incorporating parameter optimization techniques would be a natural improvement on this model.
+Moreover, it would be desirable to develop scalable algorithms that can be used to learn a topology for a large graph from signals.
+Recently, in @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn improving the over-all runtime.
+
+```{r, include=FALSE}
+knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
+```
+# Acknowledgement
+
+his work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
+Thank you to Dr.
+Robin Donatello, Ph.D., for approving this work for Data Science Capstone Project
+
+\newpage
+# References
+
+## References
+<div id="refs"></div>

### 2022-05-12 Documents/paper/notes/article_summaries.Rmd
File managment for final submission.

--- 2022-03-06 article_summaries.Rmd
@@
 ```
-
-## Literature Review
-
-Data often has  an underlying structure or Geometry that can be modeled as a signal on the vertices of a weighted, undirected graph.
-Traditionally, the emphasis was on using a the underlying graph, or network, to understand the properties of signals over the vertices.
-Recently, there has been a surge in converse problem; of learning a graph structure from a set of signals satisfying some something constraints @xia2021graph @stankovic2019vertex @ortega2018graph .
-The subset of Graph Learning that focuses on Graph Signal Processing Based Methods deals with sampling, graph recovery and learning topological structure @xia2021graph .
-The methods for learning topolological structure fall into the categories of supervised models @dong2016learning @tugnait2021sparse @pu2021learning @saboksayr2021accelerated, and unsupervised machine learning techniques @pu2021kernel @kalofolias2016learn @venkitaraman2019predicting .
-In all of these models, signals are assumed to follow multivariate gaussian distributions, but there has been little to know literature exploring learing network topology from binomial signals.
 

### 2022-05-12 Documents/paper/notes/model specification.Rmd
File managment for final submission.

--- 2022-04-19 model specification.Rmd
@@
 We assume that $Y_{i,j}$ is a binary signal that can be 1, or 0.
-Suppose the signals at round $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at round (or stratum) $k$ denoted by $Y[,k ]$, for $i \neq k$, borrowing the idea of conditional logistic regression.
+Suppose the signals at round $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at round (or stratum) $k$ denoted by $Y[,k ]$, for $j \neq k$, borrowing the idea of conditional logistic regression.
 Let $p_{i,j}$ denote the probability of $Y_{i,j} = 1$.

### 2022-05-12 Documents/poster html/poster html.Rmd
File managment for final submission.

---
title: Graph Topology Learning from Binary Signals on Graph
author:
  - name: Skip Moses
    affil: 1
  - name: Jing Guo
    affil: 1
  - name: Robin Donatello
    affil: 1
affiliation:
  - num: 1
    address: Department of Mathematics and Statistics, California State University, Chico
column_numbers: 3
# logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
# logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# Abstract

Data often has an underlying structure of geometry that can be modeled a signal on the vertices of a weighted, undirected graph. There are several analogies between traditional signal processing an algebraic graph theory that translates many of the tools of discrete signal processing such as spectral analysis of multichannel signals, system transfer function, and digital filter design to name a few. Historically, graph signal processing has focused on modeling smooth signals on a graph, but the increase in availability of abstract data sets has motivated algorithms for learning a valid graph given a set of signals. In this work we design a novel methodology for learning a valid graph topology given a set of binary signals on the graph. This is accomplished by extending the ideas of conditional logistic regression and maximum likelihood with constraints that enforce a valid graph topology.

# Introduction

Data often has  an underlying structure or geometry that can be modeled as a signal on the vertices of a weighted, undirected graph. Traditionally, the emphasis was on using a underlying graph, or network, to understand the properties of signals over the vertices. Recently, there has been a surge in converse problem; of learning a graph structure from a set of signals satisfying some constraints [@xia2021graph] [@dong2016learning] [ @ortega2018graph]. In previous research [@dong2016learning], [@tugnait2021sparse], [@pu2021learning], and [@saboksayr2021accelerated], signals on graph were assumed to follow multivariate gaussian distributions, but there has been little exploration in learning a network from binomial signals. In this work, we develop a noval methodology that allows for learning graph topology given a set of binary signals on the graph. An example of such signals on graph is presented in Figure 1.

![Figure 1. Binary Signals on Graph](bgs.PNG){width=90%}

# Methods

#### Signals on the graph and model specification
We consider a weighted undirected graph $G = (V, E)$, with the vertices set $V = {1, 2, \dots, N}$, and edge set $E$.  Let $\mathbf{A}$ denote the weighted adjacency matrix for the graph $G$. In the case of weighted undirected graph, $\mathbf{A}$ is a square and symmetric matrix.

Let $Y_{i,j}$ denote the signal on the node $i$ of graph $G$ at round $j$, where $j = 1, \dots, M$, and $i = 1, \dots, N$. We assume that $Y_{i,j}$ is a binary signal that can be 1, or 0.

Suppose the signals at stratum $j$ denoted by $Y[, j]$ for all $N$ nodes are independent of the signals at stratum $k$ denoted by $Y[,k ]$, for $j \neq k$. Let $p_{i,j}$ denote the probability of $Y_{i,j} = 1$. Our model assumes

\begin{equation}
\label{eq: binaryglm}
\text{logit}(p_{i,j}) = \alpha_j + (\mathbf{A} h )_i,
\end{equation}

where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$ and assumed to be a standard normal random vector, and $\alpha_j$ is a round specific parameter at stratum $j$, and assumed to be normally distributed with mean of 0, and unknown variance $\sigma^2$.

#### Method of Estimation
#####  Conditional likelihood for one stratum
Let $O_j$ denote the set of nodes at stratum $j$ that have observed signals of 1, and let $Z_j$ denote the set of nodes at stratum $j$ that have observed signals of 0. Suppose the number of nodes that have signals of 1 at stratum $j$ is $k_j$. The conditional likelihood function based on model (\ref{eq:binaryglm}) for stratum $j$ of size $N$, is

\begin{equation}
	\label{eq:stratumlikelihood}
	\begin{aligned}
	&	P(Y_{lj} = 1 \text{ for } l \in O_j, Y_{mj} = 0 \text{ for } m \in Z_j | \sum_{i=1}^N Y_{ij} = k_j) \\   
	& =  {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
	\end{aligned}
\end{equation}

where $C_{k_j}^N$ is the set of all subsets of size $k_j$ of the set ${1, 2, \dots, N}$.
This package uses the same workflow approach as the R Markdown you know and love. Basically it goes from RMarkdown > Knitr > Markdown > Pandoc > HTML/CSS > PDF. You can even use the bibliography the same way [].

# Results

Usually you want to have a nice table displaying some important results that you have calculated. In `posterdown` this is as easy as using the `kable` table formatting you are probably use to as per typical R Markdown formatting.

You can reference tables like so: Table \@ref(tab:mytable). Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam placerat augue at velit tincidunt semper. Donec elementum porta posuere. Nullam interdum, odio at tincidunt feugiat, turpis nisi blandit eros, eu posuere risus felis non quam. Nam eget lorem odio. Duis et aliquet orci. Phasellus nec viverra est.

```{r mytable, out.width='80%'}
knitr::kable(iris[1:10, 1:4], caption = 'Table caption.',align = 'c',"html")
```

Or with figures: Figure \@ref(fig:standard-plot), or Figure \@ref(fig:morefigs).

```{r standard-plot, out.width='80%', fig.align='center', fig.cap='Great figure!', fig.height=5}
plot(mtcars[1:2])
```

```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}
data <- iris

plot(x = data$Sepal.Length, 
     y = data$Sepal.Width, 
     col = data$Species,
     pch = 19, 
     xlab = "Sepal Length (cm)",
     ylab = "Sepal Width (cm)")

```

# Next Steps

Aliquam sed faucibus risus, quis efficitur erat. Vestibulum semper mauris quis tempus eleifend. Aliquam sagittis dictum ipsum, quis viverra ligula eleifend ut. Curabitur sagittis vitae arcu eget faucibus. In non elementum felis. Duis et aliquam nunc. Nunc pulvinar sapien nunc, vel pretium nisi efficitur in. Fusce fringilla maximus leo et maximus. Fusce at ligula laoreet, iaculis mi at, auctor odio. Praesent sed elementum justo. Aenean consectetur risus rhoncus tincidunt efficitur. Praesent dictum mauris at diam maximus maximus [].

# Conclusion

Try `posterdown` out! Hopefully you like it!

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References

### 2022-05-12 Code/binary_graph_learning/Metrics.py

@@ -1,0 +1,72 @@
+import numpy as np
+import cvxpy as cp
+import matplotlib.pyplot as plt
+from scipy import sparse
+from pygsp import graphs, filters
+from numpy.linalg import inv
+import itertools as it
+
+# Count the edges given a threshhold
+def count_edges(Lap, threshhold):
+    count = 0
+    size = Lap.shape[0]
+    for i in range(0,size):
+        for j in range(0,i):
+            if abs(Lap[i][j]) > threshhold:
+                count = count + 1
+    if count > 0:
+        return(count)
+    else:
+        return(-1)
+
+def detect_edges(L1, L2, threshhold):
+    count = 0
+    size = L1.shape[0]
+    for i in range(0,size):
+        for j in range(0,i):
+            if (abs(L1[i][j]) > threshhold) and L2[i][j] > 0:
+                count = count + 1
+    return(count)
+
+# Count the number of edges two laplacians have in common. 
+# Computes the difference and counts the number of components
+# sufficiently close to 0.
+def compare_edges_strict(L1, L2):
+    Dif = abs(L1 - L2)
+    size = Dif.shape[0]
+    count = 0
+    for i in range(0,size):
+        for j in range(0,i):
+            if Dif[i][j] < .005:
+                count = count + 1
+    return(count)
+
+# Computes the proportion of correct edges in the Learned Laplacian
+def Precision(EstL, GTL, threshhold):
+    return(detect_edges(EstL, GTL, threshhold)/count_edges(EstL, threshhold))
+
+# Computes the proportion edges in Ground truth Laplacian 
+# that appear in learned Laplacian
+def Recall(EstL, GTL, threshhold):
+    return(detect_edges(EstL, GTL, threshhold)/count_edges(GTL, 0))
+
+def F_Measure(EstL, GTL, threshhold):
+    P = Precision(EstL, GTL, threshhold)
+    R = Recall(EstL, GTL, threshhold)
+    if P+R > 0:
+        return(2*((P*R)/(P+R)))
+    else:
+        return(-1)
+
+def Relative_Error(L1, L2):
+    return(np.linalg.norm(L1 - L2)/np.linalg.norm(L1))
+
+def SSE(L1, L2):
+    return(Relative_Error(L1,L2)**2)
+
+def ComputeMetrics(EstL, GTL, threshhold):
+    return({"Precision":Precision(EstL, GTL, threshhold),
[…]

### 2022-05-12 Code/binary_graph_learning/binary_graph_learning.py

@@ -1,0 +1,69 @@
+import numpy as np
+import cvxpy as cp
+
+# Sigmoid function
+def sigmoid(x):
+    z = np.exp(-x)
+    sig = 1 / (1 + z)
+    return sig
+
+# Generates a random binary signal given a
+# h in U(-1,1) (uniform distribution) and adjacency matrix chi
+def generate_signal(h, chi):
+    P = (chi@h)
+    X = [sigmoid(p) for p in P]
+    for i in range(len(X)):
+        test = np.random.uniform(0,1)
+        if test < X[i]:
+            X[i] = 1
+        else:
+            X[i] = 0
+    return X
+
+# Used in optimization program for creating expressions
+def term_given_X(y,w,X):
+    return y.T@X@w - cp.sum(cp.logistic(X@w))
+
+def term_given_w(y,w,X):
+    return y.T@X@w - cp.sum(cp.logistic(X@w))
+
+# Given a noisy signal (Num_Nodes by Num_signals) and sparcity constraint
+# Return estimated adjacency matrix
+def binary_graph_learning(Y_noisy, alpha):
+    # Define variables 
+    Y = Y_noisy 
+    N = Y_noisy.shape[0]
+    A_var = cp.Variable((N,N), symmetric = True)
+    Lap = cp.diag(A_var@np.ones((N,1))) - A_var
+    h_var = cp.Variable((N,1))
+    h_init = np.random.uniform(-1,1,N)
+    print("CP variables built.")
+    # Adjacency Matrix Constraints
+    constraints = [cp.diag(A_var) == 0,
+                    A_var - cp.diag(cp.diag(A_var)) >= 0,
+                  sum(A_var@np.ones(N)) == N]
+    A_obj = cp.Maximize(sum([term_given_w(y,h_init,A_var) for y in Y.T]) - alpha*cp.norm(Lap, 'fro'))
+
+    P_init = cp.Problem(A_obj, constraints)
+    P_init.solve()
+    A_init = A_var.value
+    A_vals = [A_init]
+    h_vals = [h_init]
+    for i in range(10):
+        A_cur = cp.Variable((N,N), symmetric = True)
+        Lap = cp.diag(A_cur@np.ones((N,1))) - A_cur
+        h_cur = cp.Variable((N,1))
+        constraints = [cp.diag(A_cur) == 0,
+                    A_cur - cp.diag(cp.diag(A_cur)) >= 0]
[…]

### 2022-05-12 Scripts/gl_sig_rep/DuplicationM.py

@@ -1,64 +1,0 @@
-import numpy as np
-import numpy as np
-import scipy.sparse as sps
-import itril as it
-
-"""
-function M = DuplicationM(n, option)
-% function M = DuplicationM(n)
-% M = DuplicationM(n, 'lo') % (default) OR
-% M = DuplicationM(n, 'up') % 
-% Return duplication matrix order n
-%
-% It is always assumed Duplication arount main diagonal (k=0)
-%
-% Ouput are sparse
-%
-% DuplicationM(size(A),'lo')*A(itril(size(A))) == A(:) %true for lower half
-% DuplicationM(size(A),'up')*A(itriu(size(A))) == A(:) %true for upper half
-%
-% Author: Bruno Luong <brunoluong@yahoo.com>
-% Date: 21/March/2009
-%
-% Ref : Magnus, Jan R.; Neudecker, Heinz (1980), "The elimination matrix:
-% some lemmas and applications", Society for Industrial and Applied Mathematics.
-% Journal on Algebraic and Discrete Methods 1 (4): 422449,  
-% doi:10.1137/0601049, ISSN 0196-5212.
-"""
-
-def DuplicationM(n, option = 'lo'):
-    if np.isscalar(n):
-        n = [n, n]
-    
-    if option[0].lower() == 'l':
-        I, J = it.itril(n,0,False)
-    elif option[0].lower() == 'u':
-        J, I = it.itril(n,0,False)
-    else:
-        print("Error, optioin mus be 'lo' or 'up'.")
-        return()
-    
-    I = [x for _, x in sorted(zip(J, I))]
-    J = sorted(J)
-    
-    # Find the sub/sup diagonal part that can flip to other side
-    loctri = [i for i in range(len(I)) if 
-              (I[i] != J[i]) and 
-              (J[i] <= n[0]-1) and 
-              (I[i] <= n[1]-1)]
-    
-    # Indices of the flipped part
-    arg1 = [J[i] for i in loctri]
-    arg2 = [I[i] for i in loctri]
-    
-    Itransposed = np.ravel_multi_index([arg1, arg2], n)
-    
-    # Convert to linear indice
-    I = np.ravel_multi_index([I, J], n)
-    
-    arg1 = np.append(I,Itransposed)
-    arg2 = np.append([i for i in range(len(I))], loctri)
-    d = [1]*len(arg1)
-    
-    M = sps.csr_matrix((d, (arg1, arg2)), shape = (np.prod(n),len(I)))
-    return(M)

### 2022-05-12 Scripts/gl_sig_rep/Metrics.py

@@ -1,72 +1,0 @@
-import numpy as np
-import cvxpy as cp
-import matplotlib.pyplot as plt
-from scipy import sparse
-from pygsp import graphs, filters
-from numpy.linalg import inv
-import itertools as it
-
-# Count the edges given a threshhold
-def count_edges(Lap, threshhold):
-    count = 0
-    size = Lap.shape[0]
-    for i in range(0,size):
-        for j in range(0,i):
-            if abs(Lap[i][j]) > threshhold:
-                count = count + 1
-    if count > 0:
-        return(count)
-    else:
-        return(-1)
-
-def detect_edges(L1, L2, threshhold):
-    count = 0
-    size = L1.shape[0]
-    for i in range(0,size):
-        for j in range(0,i):
-            if (abs(L1[i][j]) > threshhold) and L2[i][j] < 0:
-                count = count + 1
-    return(count)
-
-# Count the number of edges two laplacians have in common. 
-# Computes the difference and counts the number of components
-# sufficiently close to 0.
-def compare_edges_strict(L1, L2):
-    Dif = abs(L1 - L2)
-    size = Dif.shape[0]
-    count = 0
-    for i in range(0,size):
-        for j in range(0,i):
-            if Dif[i][j] < .005:
-                count = count + 1
-    return(count)
-
-# Computes the proportion of correct edges in the Learned Laplacian
-def Precision(EstL, GTL, threshhold):
-    return(detect_edges(EstL, GTL, threshhold)/count_edges(EstL, threshhold))
-
-# Computes the proportion edges in Ground truth Laplacian 
-# that appear in learned Laplacian
-def Recall(EstL, GTL, threshhold):
-    return(detect_edges(EstL, GTL, threshhold)/count_edges(GTL, threshhold))
-
-def F_Measure(EstL, GTL, threshhold):
-    P = Precision(EstL, GTL, threshhold)
-    R = Recall(EstL, GTL, threshhold)
-    if P+R > 0:
-        return(2*((P*R)/(P+R)))
-    else:
-        return(-1)
-
-def Relative_Error(L1, L2):
-    return(np.linalg.norm(L1 - L2)/np.linalg.norm(L1))
-
-def SSE(L1, L2):
-    return(Relative_Error(L1,L2)**2)
-
-def ComputeMetrics(EstL, GTL, threshhold):
-    return({"Precision":Precision(EstL, GTL, threshhold),
[…]

### 2022-05-12 Scripts/gl_sig_rep/SyntheticDataGenerator.py

@@ -1,122 +1,0 @@
-import numpy as np
-import cvxpy as cp
-import matplotlib.pyplot as plt
-import networkx as nx
-from scipy import sparse
-from numpy.linalg import inv
-import itertools as it
-
-# Generate an num_signalsXnum_Vertices matrix of synthetic data
-# over a graph G following Dong's model. 
-# mu := mean; sigma := standard deviation
-def RandomSignal(graph, num_signals, mu, sigma, seed):
-    # The graph Laplacian
-    L = nx.laplacian_matrix(graph).toarray()
-    
-    # The number of vertices
-    size = L.shape[0]
-    
-    
-    # Normalized Laplacian ie tr(L) = num_vertices
-    NormL = (size/np.trace(L))*L
-    
-    # Moore Penrose Psudoinverse
-    MPPI = np.linalg.pinv(NormL, hermitian= True)
-    
-    # Vector of means
-    mean = mu*np.ones(size)
-    
-    # Matrix of standard deviation
-    stan_dev = MPPI + sigma*np.diag(np.ones(size))
-    X = []
-    for i in range(num_signals):
-        np.random.seed(seed + i)
-        signal = np.random.multivariate_normal(mean, stan_dev)
-        X.append(signal.tolist())
-    return np.transpose(X)
-    
-
-
-
-# Generates Synthetic data following Dongs Model
-# with an added regression term
-# Generate an num_signalsXnum_Vertices matrix of synthetic data
-# over a graph G following Dong's model. 
-# mu := mean; sigma := standard deviation
-def RandomRegressorSignal(graph, mu, sigma, b, P, seed):
-    # The Graph Laplacian
-    L = nx.laplacian_matrix(graph).toarray()
-    
-    # The number of vertices
-    size = L.shape[0]
-    
-    if(size != P[0].shape[0]):
-        print("Number vertices does not equal number of rows in P.")
-        return
-    if(P[0].shape[1] != b.shape[0]):
-        print("Number of columns of P[i] is not equal to number of rows of b.")
-        return
-    
-    # Normalized Laplacian ie tr(L) = num_vertices
-    NormL = (size/np.trace(L))*L
-    
-    # Moore Penrose Psudoinverse
-    MPPI = np.linalg.pinv(NormL, hermitian= True)
-    
-    # Vector of means
-    mean = mu*np.ones(size)
-    
-    # Matrix of standard deviation
-    stan_dev = MPPI + sigma*np.diag(np.ones(size))
[…]

### 2022-05-12 Scripts/gl_sig_rep/construct_graph.py

@@ -1,27 +1,0 @@
-import NetworkX as nx
-"""
-function [G, XCoords, YCoords] = construct_graph(N,opt,varargin1,varargin2)
-% Graph construction
-"""
-def construct_graph(N,opt,varagin1):
-    
-    """
-    %% construct the graph
-    switch opt
-        case 'er', % Erdos-Renyi random graph
-            p = varargin1;
-            G = erdos_reyni(N,p);
-
-        case 'pa', % scale-free graph with preferential attachment
-            m = varargin1;
-            G = preferential_attachment_graph(N,m);
-    end
-    """
-    if opt == 'er':
-        p = varargin1
-        nx.erdos_reyni_graph(N,p)
-    else:
-        m = varagin1
-        G = nx.barabasi_albert_graph(n,m)
-    return(G)
-

### 2022-05-12 Scripts/gl_sig_rep/graph_learning_gaussian.py

@@ -1,43 +1,0 @@
-import numpy as np
-import optimize_laplacian_gaussian as olg
-
-"""
-function [L,Y,L_harvard] = graph_learning_gaussian(X_noisy,param)
-% Learning graphs (Laplacian) from structured signals
-% Signals X follow Gaussian assumption
-"""
-def graph_learning_gaussian(X_noisy, param):
-    
-    N = param['N']
-    max_iter = param['max_iter']
-    alpha = param['alpha']
-    beta = param['beta']
-
-    objective = [0]*max_iter
-    Y_0 = X_noisy
-    Y = Y_0
-    
-    for i in range(max_iter):
-        
-        # Step 1: given Y, update L
-        L = olg.optimize_laplacian_gaussian(N,Y,alpha,beta)
-        
-        # Step 2: given L, update Y
-        R = np.linalg.cholesky(np.identity(N) + alpha*L)
-        Rt = np.transpose(R)
-        arg1 = np.linalg.lstsq(Rt, Y_0)[0]
-        # print('arg1 shape is ' + str(arg1.shape))
-        # print('R shape is ' + str(R.shape))
-        Y = np.linalg.lstsq(R, arg1)[0]
-        
-        # Store objective
-        arg1 = np.linalg.norm(Y-Y_0, 'fro')**2 
-        arg2 = alpha*(np.transpose((Y@np.transpose(Y)).flatten('F'))@(L.flatten('F')))
-        arg3 = beta*np.linalg.norm(L, 'fro')**2
-        objective[i] = arg1 + arg2 + arg3
-        
-        # Stopping criteria
-        if i>=2 and abs(objective(i) - objective(i-1)) < 10**(-4):
-            print(str(i) + ' iterations needed to converge.')
-            break
-        return([L.round(4), Y.round(4)])

### 2022-05-12 Scripts/gl_sig_rep/idiag.py

@@ -1,44 +1,0 @@
-import numpy as np
-
-"""
-# function [I J] = idiag(sz, k)
-# function [I J] = idiag(sz, k) # OR
-# I = itril(sz, k)
-#
-# Return the subindices [I J] (or linear indices I if single output call)
-# in the purpose of extracting the diagonal of the matrix of the size SZ.
-# Input k is optional shifting. For k=0, extract from the main
-# diagonal. For k>0 -> above the diagonal, k<0 -> below the diagonal
-#
-# Output is a column and sorted with respect to linear indice
-#
-# Example:
-#
-# A = [ 7     5     4
-#       4     2     3
-#       9     1     9
-#       3     5     7 ]
-#
-# I = idiag(size(A))  # gives [1 6 11]'
-# A(I)                # gives [7 2 9]' OR diag(A)
-#
-# Author: Bruno Luong <brunoluong@yahoo.com>
-# Date: 21/March/2009
-"""
-def idiag(sz, k = 0, linear_ind = True):
-    if np.isscalar(sz):
-        sz = [sz, sz]
-    m = sz[0]
-    n = sz[1]
-    
-    # Pay attention to clipping
-    l = 0 - min(k,0)
-    u = min(m,n-k)
-    I = list(range(l,u))
-    J = [i + k for i in I]
-    
-    if linear_ind == True: # Return Linear indices
-        I = np.ravel_multi_index([I,J], [m,n])
-        return(I)
-    return([I,J])
-    # end # idiag

### 2022-05-12 Scripts/gl_sig_rep/itril.py

@@ -1,74 +1,0 @@
-import numpy as np
-import numpy_groupies as npg
-
-# function [I J] = itril(sz, k)
-# function [I J] = itril(sz, k) # OR
-# I = itril(sz, k)
-#
-# Return the subindices [I J] (or linear indices I if single output call)
-# in the purpose of extracting an lower triangular part of the matrix of
-# the size SZ. Input k is optional shifting. For k=0, extract from the main
-# diagonal. For k>0 -> above the diagonal, k<0 -> below the diagonal
-# 
-# This returnd same as [...] = find(tril(ones(sz),k))
-# - Output is a column and sorted with respect to linear indice
-# - No intermediate matrix is generated, that could be useful for large
-#   size problem
-# - Mathematically, A(itril(size(A)) is called (lower) "half-vectorization"
-#   of A 
-#
-# Example:
-#
-# A = [ 7     5     4
-#       4     2     3
-#       9     1     9
-#       3     5     7 ]
-#
-# I = itril(size(A))  # gives [1 2 3 4 6 7 8 11 12]'
-# A(I)                # gives [7 4 9 3 2 1 5  9  7]' OR A(tril(A)>0)
-#
-# Author: Bruno Luong <brunoluong@yahoo.com>
-# Date: 21/March/2009
-
-def itril(sz, k = 0, linear_ind = True):
-    
-    if np.isscalar(sz):
-        sz = [sz, sz]
-    m = sz[0]
-    n = sz[1]
-    
-    # Main Diagonal by default
-    nc = n - max(k,0)
-    
-    lo = [int(i) for i in np.ones(nc)] # lower row indice for each column
-    
-    hi = [min(i - min(k,0), m) for i in range(1,nc+1)] # upper row indice for each column
-    
-    if len(lo) == 0: 
-        I = []
-        J = []
-    else:
-        temp = [1] + [hi[i] - lo[i] + 1 for i in range(len(hi))] 
-        c = np.cumsum(temp) # cumsum of the length
-        temp = [0] + hi[:len(hi)-1]
-        I = npg.aggregate(c[0:len(c)-1], 
-                          [lo[i] - temp[i] - 1 for i in range(len(lo))], 
-                          size = c[len(c)-1])[1:]
-        
-        I = np.cumsum([i + 1 for i in I]) # row indice
-        
-        J = npg.aggregate(c, 1)[1:]; 
-        
-        J[0] = 1 + max(k,0) # The row indices starts from this value
[…]

### 2022-05-12 Scripts/gl_sig_rep/laplacian_constraints_vech.py

@@ -1,121 +1,0 @@
-import numpy as np
-import numpy as np
-import scipy.sparse as sps
-import numpy.matlib as npm
-import DuplicationM as dm
-
-
-"""
-function [A1,b1,A2,b2,mat_obj] = laplacian_constraint_vech(N)
-% constraints        
-% mat_cons1*L == zeros(N,1)
-% mat_cons2*L <= 0
-% vec_cons3*L == N
-
-% %% matrix for constraint 1 (zero row-sum)
-% for i = 1:N
-%     tmp0{i} = sparse(1,N+1-i);
-% end
-% 
-% mat_cons1 = sparse(N,N*(N+1)/2);
-% 
-% for i = 1:N
-%     
-%     tmp = tmp0;
-%     tmp{i} = tmp{i}+1;
-%     for j = 1:i-1
-%         tmp{j}(i+1-j) = 1;
-%     end
-%     
-%     mat_cons1(i,:) = horzcat(tmp{:});
-%     
-% end
-% 
-% % for i = 1:N
-% %     mat_cons1(i,N*i-N+i-(i*(i-1)/2):N*i-(i*(i-1)/2)) = ones(1,N-i+1);
-% % end
-% % 
-% % for i = 1:N-1
-% %     xidx = i+1:N;
-% %     yidx = i*(N+N-(i-1))/2-(N-i-1):i*(N+N-(i-1))/2-(N-i-1)+N-i-1;
-% %     mat_cons1(sub2ind(size(mat_cons1),xidx,yidx)) = 1;
-% % end
-% 
-% %% matrix for constraint 2 (non-positive off-diagonal entries)
-% for i = 1:N
-%     tmp{i} = ones(1,N+1-i);
-%     tmp{i}(1) = 0;
-% end
-% 
-% mat_cons2 = spdiags(horzcat(tmp{:})',0,N*(N+1)/2,N*(N+1)/2);
-% 
-% %% vector for constraint 3 (trace constraint)
-% vec_cons3 = sparse(ones(1,N*(N+1)/2)-horzcat(tmp{:}));
-% 
-% %% matrix for objective
-% % mat_obj = sparse(N^2,N*(N+1)/2);
-% % 
-% % for i = 1:N
-% %     for j = 1:N
-% %         if j <= i-1
-% %             tmp = tmp0;
-% %             tmp{j}(i+1-j) = 1;
-% %             mat_obj((i-1)*N+j,:) = horzcat(tmp{:});
[…]

### 2022-05-12 Scripts/gl_sig_rep/optimize_laplacian_gaussian.py

@@ -1,121 +1,0 @@
-import numpy as np
-import cvxpy as cp
-import laplacian_constraints_vech as lcv
-
-"""
-function L = optimize_laplacian_gaussian(N,Y,alpha,beta)
-
-%% Laplacian constraints
-[A1,b1,A2,b2,mat_obj] = laplacian_constraint_vech(N);
-p = vec(Y*Y')';
-
-%% optimization
-cvx_begin
-
-% cvx_solver
-
-variable L(N*(N+1)/2,1)
-
-minimize alpha*p*mat_obj*L + beta*sum_square_abs(mat_obj*L)
-
-subject to
-    A1*L == b1
-    A2*L <= b2
-
-cvx_end
-
-%% convert from vector form to matrix form
-% L = convert_matrix(L,N);
-L = reshape(mat_obj*L,N,N);
-
-% %% difference vector
-% diff = zeros(1,N*(N+1)/2);
-% k = 1;
-% for i = 1:N
-%     for j = i:N
-%         diff(k) = -norm(Y(i,:)-Y(j,:),2)^2;
-%         k = k+1;
-%     end
-% end
-% 
-% %% matrix for constraint 1 (zero row-sum)
-% for i = 1:N
-%     tmp0{i} = zeros(1,N+1-i);
-% end
-% 
-% mat_cons1 = zeros(N,N*(N+1)/2);
-% 
-% for i = 1:N
-%     
-%     tmp = tmp0;
-%     tmp{i} = tmp{i}+1;
-%     for j = 1:i-1
-%         tmp{j}(i+1-j) = 1;
-%     end
-%     
-%     mat_cons1(i,:) = horzcat(tmp{:});
-%     
-% end
-% 
-% %% matrix for constraint 2 (non-positive off-diagonal entries)
-% for i = 1:N
-%     tmp{i} = ones(1,N+1-i);
-%     tmp{i}(1) = 0;
-% end
-% 
-% mat_cons2 = diag(horzcat(tmp{:}));
-% 
-% %% vector for constraint 3 (trace constraint)
-% vec_cons3 = ones(1,N*(N+1)/2)-horzcat(tmp{:});
-% 
-% %% matrix for objective
-% mat_obj = zeros(N^2,N*(N+1)/2);
-% 
-% for i = 1:N
-%     for j = 1:N
-%         if j <= i-1
-%             tmp = tmp0;
-%             tmp{j}(i+1-j) = 1;
-%             mat_obj((i-1)*N+j,:) = horzcat(tmp{:});
[…]

### 2022-05-12 Scripts/old_code/DongsAlgorithm.py

@@ -1,52 +1,0 @@
-import numpy as np
-import cvxpy as cp
-import matplotlib.pyplot as plt
-from scipy import sparse
-from pygsp import graphs, filters
-from numpy.linalg import inv
-import itertools as it
-
-def Problem1(a, b, Signal):
-    # Number of rows in our Data set.
-    num_vertices = Signal.shape[0]
-    
-    # Constant vectors of 1's and 0's
-    ONE = np.ones(num_vertices)
-    ZERO = np.zeros(num_vertices)
-    
-    # Variable for our objective function
-    Laplacian = cp.Variable((num_vertices, num_vertices), symmetric = True)
-    
-    # Constaints for valid Laplacian
-    constraints = [
-                   cp.trace(Laplacian) == num_vertices,                       
-                   Laplacian - cp.diag(cp.diag(Laplacian)) <= 0,
-                   cp.diag(Laplacian) >= 0,
-                   Laplacian@ONE == 0
-                  ]
-    
-    # Objective Function to be minimized
-    obj = cp.Minimize(a*cp.trace(Signal.transpose()@Laplacian@Signal) + 
-                      b*cp.norm(Laplacian)**2)
-    
-    prob = cp.Problem(obj, constraints)
-    prob.solve()
-    return np.matrix(Laplacian.value)
-
-def GL_SigRep(a, b, Signal, tol, max_itr):
-    Y = Signal
-    I = np.matrix(np.identity(Signal.shape[0]))
-    L = Problem1(a, b, Y)
-    for i in range(1,max_itr):
-        temp = L
-        
-        # Closed form solution given by Dong et al.
-        Y = (inv(I + a*L))@(Signal)
-        
-        # Find a new L given Y.
-        L = Problem1(a, b, Y)
-        
-        # Check if we are with in the tolerance
-        if(np.all(abs(temp - L) < tol)):
-                return np.asarray(L)
-    return np.asarray(L)

### 2022-05-12 Scripts/old_code/GSPRegression.py

@@ -1,61 +1,0 @@
-import numpy as np
-import cvxpy as cp
-import matplotlib.pyplot as plt
-from scipy import sparse
-from numpy.linalg import inv
-import itertools as it
-
-def Problem1(a, b, Signal):
-    # Number of rows in our Data set.
-    num_vertices = Signal.shape[0]
-    
-    # Constant vectors of 1's and 0's
-    ONE = np.ones(num_vertices)
-    ZERO = np.zeros(num_vertices)
-    
-    # Variable for our objective function
-    Laplacian = cp.Variable((num_vertices, num_vertices), symmetric = True)
-    
-    # Constaints for valid Laplacian
-    constraints = [
-                   cp.trace(Laplacian) == num_vertices,                       
-                   Laplacian - cp.diag(cp.diag(Laplacian)) <= 0,
-                   cp.diag(Laplacian) >= 0,
-                   Laplacian@ONE == 0
-                  ]
-    
-    # Objective Function to be minimized
-    obj = cp.Minimize(a*cp.trace(Signal.transpose()@Laplacian@Signal) + 
-                      b*cp.norm(Laplacian)**2)
-    
-    prob = cp.Problem(obj, constraints)
-    prob.solve(solver = cp.SCS)
-    return np.matrix(Laplacian.value)     
-
-def GSP_Regression(a, b, Signal, P, tol, max_itr):
-    Y = Signal
-    R = np.zeros(Y.shape)
-    I = np.matrix(np.identity(Signal.shape[0]))
-    L = Problem1(a, b, Y)
-    count = 0
-    for i in range(1,max_itr):
-        count = count + 1
-        temp = L
-        
-        # Closed form solution given by Dong et al.
-        Y = (inv(I + a*L))@(Signal - R)
-        
-        # Find new Regressor matrix
-        R = Signal - Y
-        
-        # Find a new L given Y.
-        L = Problem1(a, b, Y)
-        
-        # Check if we are within the tolerance
-        if(np.all(abs(temp - L) < tol)):
-                break
-    #b = (inv(P.transpose()@P)@P.transpose)@np.matrix.flatten(R, 'F')
-    #return [np.asarray(L), Y, b]
-    avg_dif = np.mean(temp - L)
-    print('Solution reached in ' + str(count) + ' iterations.')
-    return [np.asarray(L), Y]

### 2022-05-12 Scripts/old_code/Metrics.py

@@ -1,72 +1,0 @@
-import numpy as np
-import cvxpy as cp
-import matplotlib.pyplot as plt
-from scipy import sparse
-from pygsp import graphs, filters
-from numpy.linalg import inv
-import itertools as it
-
-# Count the edges given a threshhold
-def count_edges(Lap, threshhold):
-    count = 0
-    size = Lap.shape[0]
-    for i in range(0,size):
-        for j in range(0,i):
-            if abs(Lap[i][j]) > threshhold:
-                count = count + 1
-    if count > 0:
-        return(count)
-    else:
-        return(-1)
-
-def detect_edges(L1, L2, threshhold):
-    count = 0
-    size = L1.shape[0]
-    for i in range(0,size):
-        for j in range(0,i):
-            if (abs(L1[i][j]) > threshhold) and L2[i][j] < 0 and abs(L2[i][j]) > threshhold:
-                count = count + 1
-    return(count)
-
-# Count the number of edges two laplacians have in common. 
-# Computes the difference and counts the number of components
-# sufficiently close to 0.
-def compare_edges_strict(L1, L2):
-    Dif = abs(L1 - L2)
-    size = Dif.shape[0]
-    count = 0
-    for i in range(0,size):
-        for j in range(0,i):
-            if Dif[i][j] < .005:
-                count = count + 1
-    return(count)
-
-# Computes the proportion of correct edges in the Learned Laplacian
-def Precision(EstL, GTL, threshhold):
-    return(detect_edges(EstL, GTL, threshhold)/count_edges(EstL, threshhold))
-
-# Computes the proportion edges in Ground truth Laplacian 
-# that appear in learned Laplacian
-def Recall(EstL, GTL, threshhold):
-    return(detect_edges(EstL, GTL, threshhold)/count_edges(GTL, threshhold))
-
-def F_Measure(EstL, GTL, threshhold):
-    P = Precision(EstL, GTL, threshhold)
-    R = Recall(EstL, GTL, threshhold)
-    if P+R > 0:
-        return(2*((P*R)/(P+R)))
-    else:
-        return(-1)
-
-def Relative_Error(L1, L2):
-    return(np.linalg.norm(L1 - L2)/np.linalg.norm(L1))
-
-def SSE(L1, L2):
-    return(Relative_Error(L1,L2)**2)
-
-def ComputeMetrics(EstL, GTL, threshhold):
[…]

### 2022-05-12 Scripts/old_code/SyntheticDataGenerator.py

@@ -1,122 +1,0 @@
-import numpy as np
-import cvxpy as cp
-import matplotlib.pyplot as plt
-import networkx as nx
-from scipy import sparse
-from numpy.linalg import inv
-import itertools as it
-
-# Generate an num_signalsXnum_Vertices matrix of synthetic data
-# over a graph G following Dong's model. 
-# mu := mean; sigma := standard deviation
-def RandomSignal(graph, num_signals, mu, sigma, seed):
-    # The graph Laplacian
-    L = nx.laplacian_matrix(graph).toarray()
-    
-    # The number of vertices
-    size = L.shape[0]
-    
-    
-    # Normalized Laplacian ie tr(L) = num_vertices
-    NormL = (size/np.trace(L))*L
-    
-    # Moore Penrose Psudoinverse
-    MPPI = np.linalg.pinv(NormL, hermitian= True)
-    
-    # Vector of means
-    mean = mu*np.ones(size)
-    
-    # Matrix of standard deviation
-    stan_dev = MPPI + sigma*np.diag(np.ones(size))
-    X = []
-    for i in range(num_signals):
-        np.random.seed(seed + i)
-        signal = np.random.multivariate_normal(mean, stan_dev)
-        X.append(signal.tolist())
-    return np.transpose(X)
-    
-
-
-
-# Generates Synthetic data following Dongs Model
-# with an added regression term
-# Generate an num_signalsXnum_Vertices matrix of synthetic data
-# over a graph G following Dong's model. 
-# mu := mean; sigma := standard deviation
-def RandomRegressorSignal(graph, mu, sigma, b, P):
-    # The Graph Laplacian
-    L = nx.laplacian_matrix(graph).toarray()
-    
-    # The number of vertices
-    size = L.shape[0]
-    
-    if(size != P[0].shape[0]):
-        print("Number vertices does not equal number of rows in P.")
-        return
-    if(P[0].shape[1] != b.shape[0]):
-        print("Number of columns of P[i] is not equal to number of rows of b.")
-        return
-    
-    # Normalized Laplacian ie tr(L) = num_vertices
-    NormL = (size/np.trace(L))*L
-    
-    # Moore Penrose Psudoinverse
-    MPPI = np.linalg.pinv(NormL, hermitian= True)
-    
-    # Vector of means
-    mean = mu*np.ones(size)
-    
-    # Matrix of standard deviation
-    stan_dev = MPPI + sigma*np.diag(np.ones(size))
-    X = []
[…]

### 2022-05-26 Documents/paper/draft.Rmd
fix the figure citation

@@
 output:
-  pdf_document: default
+  bookdown::pdf_document2: default
   html_document:
@@
 
-## Introduction
+# Introduction
 
@@
 The methods for learning topological structure fall into the categories of regression like models @dong2016learning, @tugnait2021sparse, @pu2021learning, and @saboksayr2021accelerated, and machine learning techniques @pu2021kernel, @kalofolias2016learn, and  @venkitaraman2019predicting .
-In all of these models, signals are assumed to follow multivariate gaussian distributions, but there has been little exploration in learning a network from binomial signals.
+In all of these models, signals are assumed to follow multivariate Gaussian distributions, but there has been little exploration in learning a network from binomial signals.
 
@@
 
-Because \ref{eq:dongmodel} is not jointly convex, Dong et al. employ an alternating minimization scheme to solve the problem. Initially, set $Y = X$ and we find a suitable $L$ by solving 
+Because (\ref{eq:dongmodel}) is not jointly convex, Dong et al. employ an alternating minimization scheme to solve the problem. Initially, set $Y = X$ and we find a suitable $L$ by solving 
 \begin{equation}
-	\label{eq:dong:prob1}
+	\label{eq:dongprob1}
 	\begin{aligned}
@@
 
-Next, using $L$ from the first step we solve 
+Next, using $L$ from (\ref{eq:dongprob1}), we solve 
 \begin{equation}
-	\label{eq:dong:prob2}
+	\label{eq:dongprob2}
 	\begin{aligned}
@@
 
-Both \ref{eq:dong:prob1} and \ref{eq:dong:prob2} can be cast as convex optimization problems.
-Specifically, \ref{eq:dong:prob1} can be solved with the method of alternating direction of multipliers (ADMM).
+Both (\ref{eq:dongprob1}) and (\ref{eq:dongprob2}) can be cast as convex optimization problems.
+Specifically, \ref{eq:dongprob1} can be solved with the method of alternating direction of multipliers (ADMM).
 The model is applied to both synthetic and real world data, and compared to a technique used in machine learning that is similar to sparse inverse covariance estimation of Gaussian Markov Random Field models.
@@
 
-#### Signals on the graph and model specification
+## Signals on the graph and model specification
 We consider a weighted undirected graph $G = (V, E)$, with the vertices set $V = {1, 2, \dots, N}$, and edge set $E$.
@@
 
-##### Maximum likelihood for one stratum
+## Maximum likelihood for one stratum
 
@@
 
-##### Optimization Program
+## Optimization Program
 
@@
 <hr />
-\newpage
+
 # Results
-### Synthetic Data Generation
+## Synthetic Data Generation
 
@@
 
-### Graph Learning Results
+## Graph Learning Results
 
@@
 ```
+
 # Discussion
@@
 
-## References
 <div id="refs"></div>

### 2022-05-26 Documents/paper/draft.Rmd
Draft update.

@@
 ---
-title: 'Draft: Learning Laplacian from Binomial Signals'
+title: 'Graph Learning from Binomial Signals'
 author: "Skip Moses"
-date: "3/12/2022"
+date: \today
 output:
@@
 
+In this work, we suppose the odds of a node having a signal value of $1$ or $0$ depends on the signal value of its neighboring nodes in order to estimate the underlying graph topology.
+Our methodology generalizes the framework of traditional logistic regression in order to learn an adjacency matrix from a set of binary signals.
+
 ## Related Work
 
-Dong et al. propose a modified Factor Analysis model in @dong2016learning for learning a valid graph laplacian. The model proposed is given by 
+Dong et al. propose a modified factor analysis model in @dong2016learning for learning a valid graph laplacian. The model proposed is given by 
 $$x = \chi h + \mu_x + \epsilon$$
-where $h \in \mathbb{R}^N$ is the latent variable, $\mu_x \in \mathbb{R}^N$ mean of $x$.
+where $h \sim \mathcal{N}(0, \Lambda^{\dagger})$ is the latent variable,$\Lambda$ is the eigenvalue matrix of $L$, and  $\mu_x \in \mathbb{R}^N$ mean of $x$.
 The noise term $\epsilon$ is assumed to follow a multivariate Gaussian distribution with mean zero and covariance $\sigma_\epsilon^2I_N$.
@@
 Both (\ref{eq:dongprob1}) and (\ref{eq:dongprob2}) can be cast as convex optimization problems.
-Specifically, \ref{eq:dongprob1} can be solved with the method of alternating direction of multipliers (ADMM).
+Specifically, \ref{eq:dongprob1} can be solved with alternating direction method of multipliers (ADMM).
 The model is applied to both synthetic and real world data, and compared to a technique used in machine learning that is similar to sparse inverse covariance estimation of Gaussian Markov Random Field models.
 Four evaluation criteria were used  to evaluate the performance of the framework: $\textit{Precision, Recall, F-measure,}$ and $\textit{Normalized Mutual Information (NMI)}$.
-Kalofolias cites two weaknesses to this model: The use of the Frobenius norm is not amenable to interpretation, and it requires four constraints on the solution space @kalofolias2016learn.
+Kalofolias cites two weaknesses to this model: The use of the Frobenius norm on the Laplacian  has reduced interpretability, and it requires four constraints on the solution space @kalofolias2016learn.
+These extra constraints make computational scalability difficult.
 
@@
 
-The model proposed by Kalofolias is given by specifying $f(A) = -\alpha \textbf{1}^T\log(W\textbf{1}) + \beta||W||_F^2$.
+The model proposed by Kalofolias is given by specifying $f(A) = -\alpha \textbf{1}^T\log(A\textbf{1}) + \beta||A||_F^2$.
 An appealing feature of this model is the fact that for any $\lambda >0$ and solution $F(Z,\alpha, \beta)$ the following equalities hold
@@
 In @venkitaraman2019predicting machine learning concepts are employed to learn a graph from training data.
-The goal is given some data ${x_n}$ to model a target $t_n$ by the linear basis model for regression
+Let $\{x_n\}_1^N$ be a set of $N$ input observations with each $x_n$ paired with a target $t_n \in \mathbb{R}^M$.
+The authors model a set of smooth signals $y_n$ and $t_n$ via the following:
 \begin{equation}
@@
 The latter two experiments are compared the method of kernel-ridge regression (KRR) by using a normalized-mean-square-error to measure the performance of the prediction.
-It is concluded that the method is well suited for training with noise data sets that may be small.
+It is concluded that the method is well suited for training with noise data sets that may be small @venkitaraman2019predicting .
 
@@
 
-Therefore, our Likelihood function will be given by
+Therefore, our likelihood function will be given by
 
@@
 \begin{aligned}
-&\max_{\mathbf{A},h} \sum_{j = 1}^M\sum_{i=1}^N\left(y_{i,j}(\mathbf{A}[i,]h) - \log(1 + e^{\mathbf{A}[i,]h})\right) - \alpha \vert L \vert _ F \\
-\textrm{s.t.} \quad  &\mathbf{A}_{i,j} = 0 \text{ if } i =j;\,\, \mathbf{A}_{i,j} \geq 0 \text{ if } i \neq j\\
-                     &\max(h) \leq a ;  \,\, \min(h) \geq b \,\, ; \mathbb{1}h^T = 0  
+\max_{\mathbf{A},h} \phantom{..}& \sum_{j = 1}^M\sum_{i=1}^N\left(y_{i,j}(\mathbf{A}[i,]h) - \log(1 + e^{\mathbf{A}[i,]h})\right) - \alpha \vert A \vert _ F \\
+\textrm{s.t.}  & \quad \mathbf{A}_{i,j} = 0 \text{ if } i =j \\
+               & \quad \mathbf{A}_{i,j} \geq 0 \text{ if } i \neq j\\
+               & \quad h \sim \mathcal{U}(-1,1) 
 \end{aligned}
 \end{equation}
-where $\alpha$ is a tuning parameter for controlling the sparsity and $\mathbf{A}$ and $b$ are tuning parameters for restricting the spread of the values of $h$.
+where $\alpha$ is a tuning parameter for controlling the sparsity and $a$ and $b$ are tuning parameters for restricting the spread of the values of $h$.
 
@@
 &\textbf{Algorithm 1: Binary Signal Graph Learning} \\
-&1) \textbf{ Input: } \text{ Input a signal } \mathbf{Y}.\\
+&1) \textbf{ Input: } \text{ Input a signal on a graph} \mathbf{Y}.\\
 &2) \textbf{ Output: } \text{ Output an estimated } \mathbf{A}.\\
@@
 
-Let $\mathbf{A}$ be the adjacency matrix of the graph in Figure \@ref(fig:GTG), and $h \in \mathbb{R}$ be such that $h_i \sim \mathcal{N}(0,1)$.
+Let $\mathbf{A}$ be the adjacency matrix of the graph in Figure \@ref(fig:GTG), and $h \in \mathbb{R}$ be such that $h_i \sim \mathcal{U}(-1,1)$.
 Set $p$ as a logistic function of $\mathbf{A}h$, and compare $p$ to a vector $t$, where each $t_i$ follows a random uniform distribution $\mathcal{U}(0,1)$.
@@
 
-The learned graph is found with parameter values $\alpha = .2$, $a = 1$ and $b = -1$ by implementing Algorithm 1.
+The optimal $\alpha$ value, $\alpha = 0.2$ is found by performing a grid search, and selecting the $\alpha$ value that maximizes the F-measure of the learned adjacency matrix with the ground truth adjacency matrix.
+The parameter values for $a = 1$ and $b = -1$ where selected to be the ground truth values to simplify parameter optimization.
 We can see the learned adjacency matrix shares some similar features to the ground truth (left), but the learned adjacency matrix is sparser than the ground truth (right).
@@
 \newpage
-# References
 

### 2022-05-27 Documents/paper/draft.Rmd
minor changes on the draft

@@
 The key difference from traditional factor analysis is the choice of $\chi$ as a valid eigenvector matrix for a graph laplacian.
-Finding a maximum apriori estimate of $h$ reduces to solving the optimization problem
+Finding a maximum a posterior estimate of $h$ reduces to solving the optimization problem
 
@@
 &\textbf{Algorithm 1: Binary Signal Graph Learning} \\
-&1) \textbf{ Input: } \text{ Input a signal on a graph} \mathbf{Y}.\\
+&1) \textbf{ Input: } \text{ Input binary signals on a graph } \mathbf{Y}.\\
 &2) \textbf{ Output: } \text{ Output an estimated } \mathbf{A}.\\
-&3) \textbf{ Initialization: } h_{i,0} \sim \mathcal{N}(0,1) \text{ for } i = 1,\ldots, N \\
+&3) \textbf{ Initialization: } h_{i,0} \sim \mathcal{U}(-1,1) \text{ for } i = 1,\ldots, N \\
 &4) \textbf{ for } t = 1, \ldots, iter:\\
@@
 
-his work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
+This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises.
 Thank you to Dr.
@@
 
+# Reference {-}
+
 <div id="refs"></div>

### 2022-05-31 Code/binary_graph_learning/binary_graph_learning.py
Changed A to L in optimization program.

@@ -42,7 +42,7 @@ def binary_graph_learning(Y_noisy, alpha):
     constraints = [cp.diag(A_var) == 0,
                     A_var - cp.diag(cp.diag(A_var)) >= 0,
                   sum(A_var@np.ones(N)) == N]
-    A_obj = cp.Maximize(sum([term_given_w(y,h_init,A_var) for y in Y.T]) - alpha*cp.norm(Lap, 'fro'))
+    A_obj = cp.Maximize(sum([term_given_w(y,h_init,A_var) for y in Y.T]) - alpha*cp.norm(A_var, 'fro'))
 
     P_init = cp.Problem(A_obj, constraints)
     P_init.solve()

### 2023-05-22 IEEE paper/bare_jrnl.tex
Added paper in IEEE format.

--- 2022-05-27 Documents/paper/draft.Rmd
@@
----
-title: 'Graph Learning from Binomial Signals'
-author: "Skip Moses"
-date: \today
-output:
-  bookdown::pdf_document2: default
-  html_document:
-    df_print: paged
-cls: IEEEtran.cls
-bibliography: ref.bib
----
+\documentclass[journal]{IEEEtran}
+%=====================================================================
+\usepackage{amsmath,epsfig}
+\usepackage{caption}
+\usepackage{subcaption}
+%\usepackage[margin=10pt]{subfig}
+\usepackage{color}
+%\usepackage{placeins}
+\usepackage{float}
+\usepackage{tabularx,colortbl}
+\usepackage{amssymb}
+\usepackage{amsmath,graphicx}
+\usepackage{algorithm}
+\usepackage{amsfonts}
+\usepackage[noend]{algpseudocode}
+%\usepackage{multirow} %
+\usepackage{bm}
+\usepackage{eqnarray}
+\usepackage{algpseudocode}
+%\usepackage{threeparttable}
+\usepackage{hyperref}
+\usepackage{epsfig}
+\usepackage{verbatim}
+\usepackage{times}
+%\setcounter{tocdepth}{3}
+\usepackage{amsthm}
+\usepackage{empheq}
+\usepackage{euscript}
+\usepackage{fixltx2e}
+%\usepackage{isomath}
+%\usepackage[]{algorithmicx}
+\usepackage{amsthm}
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
+\usepackage{booktabs}
+%https://tex.stackexchange.com/questions/43993/ieee-latex-style-grouping-references
+\usepackage[noadjust]{cite}
+%\usepackage{balance}
+%https://tex.stackexchange.com/questions/49918/how-to-level-columns-in-bibliography
+\usepackage{flushend}
 
-# Introduction
+\usepackage[dvipsnames]{xcolor}
 
-Data often has  an underlying structure or geometry that can be modeled as a signal on the vertices of a weighted, undirected graph.
-Traditionally, the emphasis was on using a underlying graph, or network, to understand the properties of signals over the vertices.
-Recently, there has been a surge in converse problem; of learning a graph structure from a set of signals satisfying some constraints @xia2021graph @stankovic2019vertex @ortega2018graph .
-A subset of graph learning that focuses on graph signal processing based methods deals with sampling, graph recovery and learning topological structure @xia2021graph.
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+% Definition Styles
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{example}{Example}[section]
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\newcommand{\change}[1]{\textcolor{black}{#1}}
 
-The methods for learning topological structure fall into the categories of regression like models @dong2016learning, @tugnait2021sparse, @pu2021learning, and @saboksayr2021accelerated, and machine learning techniques @pu2021kernel, @kalofolias2016learn, and  @venkitaraman2019predicting .
-In all of these models, signals are assumed to follow multivariate Gaussian distributions, but there has been little exploration in learning a network from binomial signals.
+%=======================================================================================
+\ifCLASSINFOpdf
+\else
+   \usepackage[dvips]{graphicx}
+\fi
+\usepackage{url}
 
-In this work, we suppose the odds of a node having a signal value of $1$ or $0$ depends on the signal value of its neighboring nodes in order to estimate the underlying graph topology.
+\hyphenation{op-tical net-works semi-conduc-tor}
+
+\usepackage{graphicx}
+\usepackage{amsmath,amssymb}
+
+\begin{document}
+
+\title{Graph Learning from Binomial Signals'}
+
+\author{Skip Moses, Jing Guo}
+\thanks{This work was supported by the  Research, Scholarship, and Creative Activity (RSCA) Award from CSU, Chico. }
+\thanks{Skip Moses is currently a graduate student in the College of Science and Mathematics, California Polytechnic University, San Luis Obispo, CA 93407 USA (e-mail: skipmoses@gmail.com).}
+\thanks{The corresponding author Jing Guo is with the Department of Mathematics and Statistics, California State University, Chico, CA 95929 USA (e-mail: jguo2@csuchico.edu).}
+
+\markboth{IEEE SIGNAL PROCESSING LETTERS, Vol. X, 2023}
+{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
+\maketitle
+
+\begin{abstract}
+Data often has an underlying structure of Geometry that can be modeled as a signal on the vertices of a weighted, undirected graph.
+There are several analogies between traditional signal processing and algebraic graph theory that translates many of the tools of discrete signal processing such as spectral analysis of multichannel signals, system transfer function, and digital filter design to name a few.
+Historically, GSP has focused on modeling smooth signals on a graph, but the increase in the availability of abstract data sets has motivated algorithms for learning a valid graph given a set of signals.
+In this work, we attempt to design a novel methodology for learning a valid graph topology given a set of binary signals on the graph.
+This is accomplished by extending the ideas of  Logistic Regression and Maximum Likelihood with constraints that enforce a valid graph topology on the regression coefficient matrix.
+\end{abstract}
+
+\begin{IEEEkeywords}
+graph learning, graph signal processing, binary signals, logistic regression, Laplacian matrix
+\end{IEEEkeywords}
+
+\section{Introduction}
+
+\IEEEPARstart{D}{ata} often has an underlying structure or geometry that can be modeled as a signal on the vertices of a weighted, undirected graph.
+Traditionally, the emphasis was on using an underlying graph, or network, to understand the properties of signals over the vertices.
+Recently, there has been a surge in the converse problem; of learning a graph structure from a set of signals satisfying some constraints \cite{xia2021graph} \cite{stankovic2019vertex} \cite{ortega2018graph}.
+A subset of graph learning that focuses on graph signal processing-based methods deals with sampling, graph recovery, and learning topological structure \cite{xia2021graph}.
+
+The methods for learning topological structure fall into the categories of regression-like models \cite{dong2016learning}, \cite{tugnait2021sparse}, \cite{pu2021learning}, and \cite{saboksayr2021accelerated}, and machine learning techniques \cite{pu2021kernel}, \cite{kalofolias2016learn}, and  \cite{venkitaraman2019predicting}.
+In all of these models, signals are assumed to follow multivariate Gaussian distributions, but there has been little exploration into learning a network from binomial signals.
+
+In this work, we suppose the odds of a node having a signal value of $1$ or $0$ depend on the signal value of its neighboring nodes in order to estimate the underlying graph topology.
 Our methodology generalizes the framework of traditional logistic regression in order to learn an adjacency matrix from a set of binary signals.
 
-## Related Work
+\section{Related Work}
 
-Dong et al. propose a modified factor analysis model in @dong2016learning for learning a valid graph laplacian. The model proposed is given by 
-$$x = \chi h + \mu_x + \epsilon$$
+Dong et al. propose a modified factor analysis model in \cite{dong2016learning} for learning a valid graph laplacian. The model proposed is given by
+
+$$
+	x = \chi h + \mu_x + \epsilon
+$$
+
 where $h \sim \mathcal{N}(0, \Lambda^{\dagger})$ is the latent variable,$\Lambda$ is the eigenvalue matrix of $L$, and  $\mu_x \in \mathbb{R}^N$ mean of $x$.
@@
 Both (\ref{eq:dongprob1}) and (\ref{eq:dongprob2}) can be cast as convex optimization problems.
-Specifically, \ref{eq:dongprob1} can be solved with alternating direction method of multipliers (ADMM).
-The model is applied to both synthetic and real world data, and compared to a technique used in machine learning that is similar to sparse inverse covariance estimation of Gaussian Markov Random Field models.
+Specifically, \ref{eq:dongprob1} can be solved with the alternating direction method of multipliers (ADMM).
+The model is applied to both synthetic and real-world data, and compared to a technique used in machine learning that is similar to sparse inverse covariance estimation of Gaussian Markov Random Field models.
 Four evaluation criteria were used to evaluate the performance of the framework: $\textit{Precision, Recall, F-measure,}$ and $\textit{Normalized Mutual Information (NMI)}$.
-Kalofolias cites two weaknesses to this model: The use of the Frobenius norm on the Laplacian  has reduced interpretability, and it requires four constraints on the solution space @kalofolias2016learn.
+Kalofolias cites two weaknesses to this model: The use of the Frobenius norm on the Laplacian has reduced interpretability, and it requires four constraints on the solution space \cite{kalofolias2016learn}.
 These extra constraints make computational scalability difficult.
 
-In @kalofolias2016learn, Kalofolias provides complementary ideas to improve on the work of Dong et al.
-In particular, Kalofolias considers the more natural problem of leaning the weighted adjacency matrix $A$, and show an extra smoothness condition leads to the learned graph being sparse.
+In \cite{kalofolias2016learn}, Kalofolias provides complementary ideas to improve on the work of Dong et al.
+In particular, Kalofolias considers the more natural problem of learning the weighted adjacency matrix $A$, and show an extra smoothness condition leads to the learned graph being sparse.
 Define, $Z$ to be the matrix of pairwise distances of the signal, namely, $Z_{i,j} = ||x_i - x_j||^2$.
-Under this definition we can recast our smoothness term as
+Under this definition, we can recast our smoothness term as
 \begin{equation}
@@
 
-In @venkitaraman2019predicting machine learning concepts are employed to learn a graph from training data.
+In \cite{venkitaraman2019predicting} machine learning concepts are employed to learn a graph from training data.
 Let $\{x_n\}_1^N$ be a set of $N$ input observations with each $x_n$ paired with a target $t_n \in \mathbb{R}^M$.
@@
 The input $x_n$ does not have to be a signal over the graph and can even be agnostic to a graph.
-The cost function for the model when the underlying graph is known is given by
+The cost function for the model, when the underlying graph is known, is given by
 \begin{equation}
@@
 Next, it is shown KRG induces a smoothing effect on the target by a shrinkage in the direction of eigenvectors of $L$ that have eigenvalues less than $\alpha$.
-In order to learn an unknown graph, a term is added to the cost function $C(\textbf{W}, L) = C(\textbf{W}) + \nu \text{tr}(L^TL)$.
+To learn an unknown graph, a term is added to the cost function $C(\textbf{W}, L) = C(\textbf{W}) + \nu \text{tr}(L^TL)$.
 Venkitarman et al.
-use the model to predict temperature using air-pressure observations collected in Sweden, next day temperature from current day in Sweden, and fMRI voxel intensities of the cerebellum region.
-The latter two experiments are compared the method of kernel-ridge regression (KRR) by using a normalized-mean-square-error to measure the performance of the prediction.
-It is concluded that the method is well suited for training with noise data sets that may be small @venkitaraman2019predicting .
+uses the model to predict temperature using air-pressure observations collected in Sweden, next-day temperature from the current day in Sweden, and fMRI voxel intensities of the cerebellum region.
+The latter two experiments are compared to the method of kernel-ridge regression (KRR) by using a normalized-mean-square error to measure the performance of the prediction.
+It is concluded that the method is well suited for training with noise data sets that may be small \cite{venkitaraman2019predicting}.
 
-## Preliminaries
+\section{Preliminaries}
 
@@
 \end{equation} 
-The Laplacian is positive semi definite, so it has a complete set of orthornormal eigenvectors, and real non negative eigenvalues.
-Thus, we can diagonalize $L = \chi^T\Lambda \chi$ where $\Lambda$ is the diagonal matrix of eigenvalues and $\chi$ is associated matrix of eigenvectors.
+The Laplacian is positive and semi-definite, so it has a complete set of orthonormal eigenvectors and real nonnegative eigenvalues.
+Thus, we can diagonalize $L = \chi^T\Lambda \chi$ where $\Lambda$ is the diagonal matrix of eigenvalues and $\chi$ is the associated matrix of eigenvectors.
 
@@
 This makes \ref{eq:quadraticform} well suited for measuring the smoothness of a signal on a graph.
-We can cast the problem of learning a graph by the optimization problem found in @kalofolias2016learn
+We can cast the problem of learning a graph by the optimization problem found in \cite{kalofolias2016learn}
 \begin{equation}
@@
 
-# Methods
+\section{Methods}
 
-## Signals on the graph and model specification
+\subsection{Signals on the graph and model specification}
+
 We consider a weighted undirected graph $G = (V, E)$, with the vertices set $V = {1, 2, \dots, N}$, and edge set $E$.
 Let $\mathbf{A}$ denote the weighted adjacency matrix of $G$.
-In the case of weighted undirected graph, $\mathbf{A}$ is a square and symmetric matrix.
+In the case of a weighted undirected graph, $\mathbf{A}$ is a square and symmetric matrix.
 
 Let $\mathbf{Y}_{i,j}$ denote the signal on the node $i$ of graph $G$ at round $j$, where $j = 1, \dots, M$, and $i = 1, \dots, N$.
-We assume that $\mathbf{Y}_{i,j}$ is a binary signal that can be 1, or 0.
+We assume that $\mathbf{Y}_{i,j}$ is a binary signal that can be 1 or 0.
 Suppose the signals at stratum $j$ denoted by $\mathbf{Y}[, j]$ for all $N$ nodes are independent of the signals at stratum $k$ denoted by $\mathbf{Y}[,k ]$, for $j \neq k$.
@@
 
-## Maximum likelihood for one stratum
+\subsubsection{Maximum likelihood for one stratum}
 
@@
 
-## Optimization Program
+\subsubsection{Optimization Program}
 
@@
 \begin{aligned}
-\max_{\mathbf{A},h} \phantom{..}& \sum_{j = 1}^M\sum_{i=1}^N\left(y_{i,j}(\mathbf{A}[i,]h) - \log(1 + e^{\mathbf{A}[i,]h})\right) - \alpha \vert A \vert _ F \\
+\max_{\mathbf{A},h} \phantom{..}& \sum_{j = 1}^M\sum_{i=1}^N\left(y_{i,j}(\mathbf{A}[i,]h) - \log(1 + e^{\mathbf{A}[i,]h})\right) - \alpha \vert L \vert _ F \\
 \textrm{s.t.}  & \quad \mathbf{A}_{i,j} = 0 \text{ if } i =j \\
@@
 
-We presented our optimization algorithm below.
-In each iteration of step 5) and 6) of Algorithm 1, the optimization program gives a Disciplined Concave Program that can be solved efficiently in Python with the CVXPY library.
+\subsubsection{Algorithm}
 
-<hr />
+We present our optimization algorithm below.
+In each iteration of steps 5) and 6) of Algorithm 1, the optimization program gives a Disciplined Concave Program that can be solved efficiently in Python with the CVXPY library.
+
 \begin{align*}
@@
 \end{align*}
-<hr />
 
-# Results
-## Synthetic Data Generation
+\section{Results}
 
-```{r GTG, echo=FALSE,out.width="80%", out.height="25%",fig.cap ="The ground truth graph with an example signal shown.",fig.show='hold',fig.align='center'}
-knitr::include_graphics(c("pictures/gt_graph.png"))
-```
+\subsection{Synthetic Data Generation}
 
-Let $\mathbf{A}$ be the adjacency matrix of the graph in Figure \@ref(fig:GTG), and $h \in \mathbb{R}$ be such that $h_i \sim \mathcal{U}(-1,1)$.
+\begin{figure}
+  \includegraphics[width=\linewidth]{pictures/gt_graph.png}
+  \caption{Ground truth graph used to generate synthetic data.}
+  \label{fig:gt}
+\end{figure}
+
+Let $\mathbf{A}$ be the adjacency matrix of the graph in Figure \ref(fig:GTG), and $h \in \mathbb{R}$ be such that $h_i \sim \mathcal{U}(-1,1)$.
 Set $p$ as a logistic function of $\mathbf{A}h$, and compare $p$ to a vector $t$, where each $t_i$ follows a random uniform distribution $\mathcal{U}(0,1)$.
 If $t_k < p_k$, then node $k$ takes the signal value of $1$, and $0$ otherwise.
-We generate $M = 100$ synthetic signals, and use them to learn an adjacency matrix.
+We generate $M = 100$ synthetic signals and use them to learn an adjacency matrix.
 
-## Graph Learning Results
+\subsection{Graph Learning Results}
 
-The optimal $\alpha$ value, $\alpha = 0.2$ is found by performing a grid search, and selecting the $\alpha$ value that maximizes the F-measure of the learned adjacency matrix with the ground truth adjacency matrix.
-The parameter values for $a = 1$ and $b = -1$ where selected to be the ground truth values to simplify parameter optimization.
+The optimal $\alpha$ value, $\alpha = 0.2$ is found by performing a grid search and selecting the $\alpha$ value that maximizes the F-measure of the learned adjacency matrix with the ground truth adjacency matrix.
+The parameter values for $a = 1$ and $b = -1$ were selected to be the ground truth values to simplify parameter optimization.
 We can see the learned adjacency matrix shares some similar features to the ground truth (left), but the learned adjacency matrix is sparser than the ground truth (right).
 
-```{r HM, echo=FALSE,out.width="49%", out.height="20%",fig.cap="(Left) A heatmap of the ground truth adjacency matrix.
-(Right) A heatmap of the estimated adjacency matrix.
-",fig.show='hold',fig.align='center'}
-knitr::include_graphics(c("pictures/gt_A_heatmap.png","pictures/est_A_heatmap.png"))
-```
+\begin{figure}[h!]
+  \centering
+  \begin{subfigure}[b]{0.4\linewidth}
+    \includegraphics[width=\linewidth]{pictures/gt_A_heatmap.png}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.4\linewidth}
+    \includegraphics[width=\linewidth]{pictures/est_A_heatmap.png}
+  \end{subfigure}
+  \label{fig:heatmap}
+\end{figure}
 
-```{r EAG, echo=FALSE,out.width="80%", out.height="25%",fig.cap="Circular Embedding of Estimated graph.
-Note the overall weight of each edge is smaller than the edge weights of the ground truth.",fig.show='hold',fig.align='center'}
-knitr::include_graphics(c("pictures/est_graph.png"))
-```
+\begin{figure}
+  \includegraphics[width=\linewidth]{pictures/gt_graph.png}
+  \caption{Graph estimated from synthetic data.}
+  \label{fig:gt}
+\end{figure}
 
-# Discussion
+\section{Discussion}
+
 To our knowledge, this is the first work on learning graph topology from binary signals.
@@
 This model can be easily extended for learning binomial signals in general.
-Incorporating parameter optimization techniques would be a natural improvement on this model.
+Incorporating parameter optimization techniques would be a natural improvement in this model.
 Moreover, it would be desirable to develop scalable algorithms that can be used to learn a topology for a large graph from signals.
-Recently, in @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn improving the over-all runtime.
+Recently, in \cite{saboksayr2021accelerated} the author shows fast proximal-gradient iterations can be applied to the framework given by \cite{kalofolias2016learn} improving the overall runtime.
 
-```{r, include=FALSE}
-knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
-```
-# Acknowledgement
+\section*{Acknowledgment}
 
@@
 Thank you to Dr.
-Robin Donatello, Ph.D., for approving this work for Data Science Capstone Project
+Robin Donatello, Ph.D., for approving this work for Data Science Capstone Project.
 
@@
 
-# Reference {-}
+\bibliographystyle{IEEEtran}
+\bibliography{rgl}
 
-<div id="refs"></div>
+\end{document}

### 2023-05-23 IEEE paper/GL_binary.tex
fix reference and front page

--- 2023-05-22 IEEE paper/bare_jrnl.tex
@@
 \title{Graph Learning from Binomial Signals'}
-
-\author{Skip Moses, Jing Guo}
+\author{Skip Moses, Jing Guo
 \thanks{This work was supported by the  Research, Scholarship, and Creative Activity (RSCA) Award from CSU, Chico. }
 \thanks{Skip Moses is currently a graduate student in the College of Science and Mathematics, California Polytechnic University, San Luis Obispo, CA 93407 USA (e-mail: skipmoses@gmail.com).}
-\thanks{The corresponding author Jing Guo is with the Department of Mathematics and Statistics, California State University, Chico, CA 95929 USA (e-mail: jguo2@csuchico.edu).}
+\thanks{The corresponding author Jing Guo is with the Department of Mathematics and Statistics, California State University, Chico, CA 95929 USA (e-mail: jguo2@csuchico.edu).}}
 
@@
 \bibliographystyle{IEEEtran}
-\bibliography{rgl}
+\bibliography{ref}
 
